### 2024-11-25 paper/Exploring_the_Determinants_of_Body_Weight.qmd
Add files via upload

---
title: "Exploring the Determinants of Body Weight: A Bayesian Analysis of Anthropometric and Demographic Factors Among Female U.S. Army Personnel"
subtitle: "Identifying Key Predictors to Enhance Health Monitoring and Operational Readiness"
author: 
  - aa
thanks: "Code and data are available at: "
date: today
date-format: long
abstract: "This study examines the relationship between body weight and key anthropometric and demographic factors among female U.S. Army personnel using a Bayesian regression model. The analysis found that waist circumference and thigh circumference are strong predictors of body weight, while other variables, such as height, age, and military component, show weaker or uncertain associations. These findings highlight the importance of body composition measurements in understanding weight variation and support their use in designing health monitoring programs and military equipment. By identifying key predictors, this research contributes to improving fitness assessments and operational readiness in physically demanding occupations."
format: pdf
number-sections: true
bibliography: references.bib
---

# Introduction {#sec-intro}

Body weight is a critical factor influencing physical performance, health, and operational readiness, especially in physically demanding occupations like military service. Within the U.S. Army, maintaining optimal weight is vital for soldiers to meet physical fitness standards, minimize injury risks, and ensure the success of military operations. Furthermore, excessive weight can increase healthcare costs and compromise operational efficiency, underscoring the importance of understanding the factors that contribute to variations in body weight. Despite the extensive data collected on anthropometric and demographic characteristics of military personnel, there is limited research examining how these factors collectively influence body weight among U.S. Army soldiers, particularly female personnel.

This study aims to fill this gap by leveraging the 2012 U.S. Army Anthropometric Survey (ANSUR II) Female Dataset, a comprehensive collection of anthropometric and demographic measurements of female Army personnel. Specifically, the study focuses on identifying key anthropometric and demographic predictors of body weight and developing a predictive model to enhance health monitoring, fitness interventions, and equipment design. By examining relationships between body weight and variables such as height, waist circumference, and demographic factors like age and ethnicity, this research offers new insights into the determinants of body weight in a physically demanding workforce.

Our findings reveal that a combination of anthropometric measurements, including height, waist circumference, and upper and lower body circumferences, significantly predict body weight. Demographic factors, such as age and ethnicity, also contribute to variations in weight, highlighting the interplay between biological and environmental factors. The predictive model developed in this study demonstrates strong performance, offering practical applications for designing personalized fitness programs, improving health outcomes, and optimizing military gear.

This paper is organized as follows: Section 2 reviews the methodology, including the selection of variables and statistical approach. Section 3 presents the results, focusing on the significance of predictors and model performance. Section 4 discusses the implications of the findings for military readiness, health interventions, and equipment design. Finally, Section 5 concludes with the study’s contributions, limitations, and suggestions for future research.

## Estimand

This study estimates the relationship between body weight and key anthropometric and demographic variables among female U.S. Army personnel. It quantifies how variations in measurements like height and waist circumference, and factors such as age and ethnicity, influence body weight, aiming to identify significant predictors and develop a robust predictive model.

# Data {#sec-data}

```{r}
#| echo: false
#| warning: false
#| message: false

library(tidyverse)
library(tinytable)
library(dplyr)
library(arrow)
library(knitr)
library(ggplot2)

# Load the dataset
file_path <- "../data/analysis-data/ansur_female_data.csv" 
ansur_female <- read_csv(file_path)

```

## Measurement

The dataset used in this study is the 2012 U.S. Army Anthropometric Survey (ANSUR II) Female Dataset, which provides detailed anthropometric and demographic measurements of 1,986 female U.S. Army personnel. The data collection was conducted by the Natick Soldier Research, Development and Engineering Center (NSRDEC) between 2010 and 2012, using standardized protocols to ensure consistency and reliability.

Anthropometric measurements were collected using precise tools such as stadiometers, measuring tapes, and calipers, ensuring accurate capture of variables like stature (height in cm), waist circumference, chest circumference, and biceps circumference (flexed). For example, stature was measured with participants standing upright, waist circumference at the narrowest point of the torso, and chest circumference at its widest point. These methods ensured that the physical measurements reflected real-world body compositions with minimal error.

Demographic variables, including age, ethnicity, and component (Active Duty, Reserves, or National Guard), were self-reported and cross-verified with administrative records to ensure accuracy. This meticulous process ensured that both physical and demographic data were reliable for analysis.

Data preprocessing for this study involved cleaning and organizing the dataset to focus on variables relevant to predicting body weight. This included removing implausible outliers, ensuring uniformity in measurement units, and verifying data completeness. The clean dataset was analyzed and modeled using R, leveraging the following packages:

-   `tidyverse`: For efficient data manipulation and visualization.

-   `ggplot2`: To create detailed and insightful visualizations.

-   `dplyr`: For transforming and summarizing the dataset effectively.

-   `broom`: For tidying model outputs and integrating them into analysis workflows.

-   `caret`: To support the modeling and evaluation of predictive models.

-   `knitr`: For creating dynamic, reproducible reports.

```{r}
#| label: tbl-head-data
#| tbl-cap: Table of first 6 rows of the cleaned dataset
#| echo: false
#| warning: false
#| message: false

ansur_female |>
  head() |>
  kable(booktabs = TRUE, align = "c")
```

## Outcome Variable

#### Body Weight in Pounds {#sec-body-weight}

The outcome variable for this study is weightlbs, which measures the body weight of female U.S. Army personnel in pounds. This variable represents the total body mass of an individual and serves as the dependent variable in the analysis. Understanding variations in body weight is crucial for examining physical readiness, health risks, and the design of military equipment tailored to individual needs.

\@fig-weight-distribution illustrates the distribution of body weight among the sample population. The histogram shows that most individuals weigh between 120 lbs and 160 lbs, with the distribution displaying a slight right skew. This skew indicates the presence of a few individuals with higher body weights, though these are relatively uncommon.

```{r}
#| label: fig-weight-distribution
#| fig-cap: The distribution of body weight among female U.S. Army personnel, showing a central tendency around 120-160 lbs with a slight right skew.
#| echo: false
#| warning: false
#| message: false

ggplot(data = ansur_female, aes(x = weightlbs)) +
  geom_histogram(binwidth = 2, fill = "steelblue", color = "grey50") +
  labs(
    x = "Body Weight (lbs)",
    y = "Count"
  ) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5))

```

## Predictor Variables

#### Height {#sec-height}

Height, measured as heightin in inches, is one of the primary predictors of body weight. Taller individuals typically have larger skeletal structures and more body mass, making height a critical variable in understanding variations in weight.

\@fig-height-distribution shows the distribution of height among the sample population. Most individuals have heights clustered between 58 inches and 71 inches, with a central tendency around 63 inches. The distribution appears approximately normal if despite the outliers of person above 73 inches, which aligns with expected variations in height for adult females.

```{r}
#| label: fig-height-distribution
#| fig-cap: The distribution of height (inches) among female U.S. Army personnel, centered around 63 inches.
#| echo: false
#| warning: false
#| message: false

ggplot(data = ansur_female, aes(x = heightin)) +
  geom_histogram(binwidth = 2, fill = "darkgreen", color = "grey50") +
  labs(
    x = "Height (inches)",
    y = "Count"
  ) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5))

```

#### Waist Circumference {#sec-waist-circumference}

Waist circumference is a key anthropometric variable that reflects abdominal fat distribution and overall body composition. In this dataset, waist_circumference was measured at the narrowest part of the torso using a flexible measuring tape, ensuring accuracy and consistency.

Waist circumference is a strong predictor of body weight due to its association with abdominal fat and overall body mass. This variable is expected to show a moderate to strong positive correlation with weight, particularly as it reflects adiposity and central body composition.

@fig-waist-thigh-violin-plots The violin plot shows that most values are concentrated between approximately 65 cm and 90 cm, with a central tendency around the mid-point of this range. Outliers are present above 115 cm, indicating a small number of individuals with unusually large waist circumferences. The overall spread (interquartile range) is moderate.

#### Thigh Circumference {#sec-thigh-circumference}

Thigh circumference measures the size of the upper leg, reflecting both muscle mass and fat distribution in the lower body. In this dataset, thigh_circumference was measured at the largest part of the thigh using a flexible measuring tape, ensuring consistency.

@fig-waist-thigh-violin-plots shows the distribution is slightly narrower than that of waist circumference, with most values falling between 50 cm and 65 cm, The median appears to be around 61 cm. A few outliers exist above 75 cm, representing individuals with larger thigh circumferences.

Thigh circumference provides insight into lower body muscle and fat distribution, making it an important predictor of weight. This variable is expected to have a positive correlation with body weight, as larger thigh circumferences typically indicate greater body mass.

```{r}
#| label: fig-waist-thigh-violin-plots
#| fig-cap: "Figure: Violin plots showing the distribution of waist and thigh circumferences, with individual data points overlaid to provide a detailed visualization of the data spread."
#| echo: false
#| warning: false
#| message: false

# Example dataset (use your cleaned data instead)
data <- ansur_female

# Reshape the data for easier plotting
data_long <- data |> 
  tidyr::pivot_longer(
    cols = c(waist_circumference, thigh_circumference),
    names_to = "measurement",
    values_to = "value"
  )

# Create violin plots
ggplot(data_long, aes(x = measurement, y = value, fill = measurement)) +
  geom_violin(trim = FALSE, alpha = 0.7) +  # Violin plot with full tails
  geom_jitter(width = 0.2, alpha = 0.5, color = "black") +  # Overlay actual data points
  theme_minimal() +
  labs(
    title = "Distribution of Waist and Thigh Circumference",
    x = "Measurement",
    y = "Circumference (in mm)",
    fill = "Measurement"
  ) +
  theme(legend.position = "none")

```

#### Age {#sec-age}

Age is a critical demographic variable in this study, reflecting biological and lifestyle factors that influence body weight. As individuals age, changes in metabolism, muscle mass, and fat distribution can impact body composition. In the dataset, age is measured in years and was self-reported by participants, with additional verification through administrative records to ensure accuracy.

@tbl-age-distribution illustrates the distribution of age within the sample population. Most individuals are between 22 and 34 years old, with a noticeable peak around the late 20s.

```{r}
#| label: tbl-age-distribution
#| tbl-cap: The table showing distribution of age among female U.S. Army personnel, with most individuals between 22 and 34 years old.
#| echo: false
#| warning: false
#| message: false

# Summary statistics for age
age_summary <- ansur_female %>%
  summarise(
    Min = min(age, na.rm = TRUE),
    `1st Quartile` = quantile(age, 0.25, na.rm = TRUE),
    Median = median(age, na.rm = TRUE),
    `3rd Quartile` = quantile(age, 0.75, na.rm = TRUE),
    Max = max(age, na.rm = TRUE),
    Mean = mean(age, na.rm = TRUE),
    SD = sd(age, na.rm = TRUE)
  )

cap <- "Summary of Age Distribution"
not <- "The table showing distribution of age among female U.S. Army personnel, with most individuals between 22 and 34 years old."
# Convert summary to a tinytable
age_table <- tt(age_summary, caption = cap, notes = not)

# Display the table
age_table

```

#### Component {#sec-component}

Component refers to the military branch or service type (e.g., Active Duty, Reserves, or National Guard) of the female U.S. Army personnel. This demographic variable is categorical and provides insight into lifestyle and activity differences that may influence body weight. For instance, Active Duty personnel may have different physical fitness levels compared to those in the Reserves or National Guard due to varying levels of daily activity and training regimens.

\@tbl-component-distribution shows the distribution of military components among female U.S. Army personnel, categorized as Regular Army, Army Reserve, and National Guard. The Regular Army comprises the majority (51.36%, 1,020 individuals), reflecting high physical activity levels due to daily duties and training. The National Guard represents 42.65% (847 individuals), with more variable schedules balancing civilian and military roles. The Army Reserve, the smallest group (5.99%, 119 individuals), likely experiences intermittent physical activity due to less frequent training requirements.

```{r}
#| label: tbl-component-distribution
#| tbl-cap: The table showing the distribution of military components (Regular Army, Reserves, National Guard) among female U.S. Army personnel.
#| echo: false
#| warning: false
#| message: false

# Frequency table for component
component_summary <- ansur_female %>%
  count(component) %>%
  mutate(Percentage = round(n / sum(n) * 100, 2))

# Convert to tinytable
cap <- "Summary of components Distribution"
not <- 'Distribution of military components are categorized as Regular Army, Reserves, and National Guard.'
component_table <- tt(component_summary, caption = cap, notes = not)

# Display the table
component_table

```

# Model

## Bayesian Regression Model

To analyze the relationship between body weight and selected predictors, a Bayesian regression model was constructed using the cleaned ANSUR II Female data. The Bayesian regression model uses a Gaussian likelihood function. The model is based on a total of 1000 observations, randomly sampled from the cleaned dataset. We run the model in R [@citeR] using the `rstanarm` package of @rstanarm, taking advantage of its efficient Bayesian estimation techniques for continuous outcome variables. The model uses weight (kg) as the dependent variable and the following predictors:

1.  Height (cm): Reflects body size and overall skeletal structure.

2.  Waist Circumference (cm): Indicates abdominal fat and body composition.

3.  Thigh Circumference (cm): Captures lower body fat and muscle mass distribution.

4.  Age (years): Accounts for biological and lifestyle changes over time.

5.  Component (categorical): Differentiates between Active Duty, Reserves, and National Guard personnel.

## Model Set-up

Let $y_i$ represent the continuous variable weight (in lbs) for the $i$-th individual in the sample. The predictors in the model include:

-   $\beta_1$: The coefficient for height, measured in inches, representing overall body structure and skeletal size.

-   $\beta_2$: The coefficient for waist circumference, which reflects abdominal fat and overall body composition.

-   $\beta_3$: The coefficient for thigh circumference, capturing lower body muscle and fat distribution.

-   $\beta_4$: The coefficient for age, measured in years, accounting for changes in body composition over time.

-   $\beta_5$: The coefficient for component, a categorical variable indicating military branch (Regular Army, Reserves, or National Guard).

Each coefficient $\beta_j$ represents the effect of the $j$-th predictor on body weight, expressed as the expected change in weight associated with a one-unit increase in the predictor, while holding all other variables constant.

The linear predictor $\eta_i$ for the $i$-th observation is defined as:

$\eta_i = \beta_0 + \beta_1 \cdot \text{height}_i + \beta_2 \cdot \text{waist circumference}_i + \beta_3 \cdot \text{thigh circumference}_i + \beta_4 \cdot \text{age}_i + \beta_5 \cdot \text{component}_i$​

The model assumes a Gaussian likelihood for $y_i$, with:

$y_i \sim \mathcal{N}(\eta_i, \sigma^2)$

Where:

-   $\beta_0$: The intercept, representing the baseline body weight when all predictors are zero.

-   $\sigma^2$: The residual variance, capturing the variability in body weight not explained by the predictors.

## Prior Distributions

In the Bayesian regression model implemented using the rstanarm package, default priors are applied to the model parameters to ensure robust and reliable inference. These priors are designed to be weakly informative, balancing the need for regularization with flexibility to adapt to the data:

-   Intercept Priors: For the model’s intercept $\beta_0$, a normal prior distribution is used with a mean of 0 and a standard deviation of 1. This prior helps stabilize the intercept estimate without imposing overly strong assumptions about its central value.

-   Coefficient Priors: Coefficients for the predictor variables $\beta_1, \beta_2, \beta_3, \beta_4, \beta_5$ are assigned normal prior distributions with a mean of 0 and a standard deviation of 1. These priors limit the possibility of overly large coefficient estimates unless strongly supported by the data, introducing a level of regularization to prevent overfitting.

The priors are intentionally weakly informative to provide flexibility while maintaining some level of regularization, ensuring that the model remains robust to overfitting. The rstanarm package handles the specification and implementation of these priors, making Bayesian inference accessible for a wide range of applications. By incorporating these priors, the model can better capture the relationships between predictors and body weight, producing credible parameter estimates and uncertainty quantification.

# Results

## Model Justification

The Bayesian regression model was developed to understand the relationship between body weight and anthropometric and demographic predictors among female U.S. Army personnel. The predictors included height, waist circumference, thigh circumference, age, and military component. The analysis revealed that anthropometric measurements, particularly height, waist circumference, and thigh circumference, have significant positive associations with body weight, while age and component showed smaller but meaningful effects. These findings are summarized in @tbl-bayesian-model-summary.

```{r}
#| echo: false
#| warning: false
#| message: false

library(rstanarm)
ansur_bayesian_model <-
  readRDS(file = here::here("models/ansur_bayesian_model.rds"))

```

```{r}
#| label: tbl-bayesian-model-summary
#| tbl-cap: Bayesian Regression Model Results.
#| echo: false
#| warning: false
#| message: false

# Load required libraries
library(modelsummary)

# Create a summary table using modelsummary
modelsummary(
  list("Bayesian Regression Model" = ansur_bayesian_model),
  statistic = c("conf.int", "std.error"), # Include credible intervals and standard errors
  stars = FALSE,                         # Disable statistical significance stars
  gof_omit = ".*"
)

```

The coefficient summary presented in @tbl-bayesian-model-summary reflects the relationships between body weight and selected predictors among female U.S. Army personnel. For instance, waist circumference and thigh circumference show positive mean coefficients, suggesting their roles as key indicators of body weight, with increases in these measurements associated with higher body weight. These findings align with the expected relationship between anthropometric dimensions and overall body mass.

Conversely, the coefficients for age and height exhibit weak associations, with credible intervals that include zero, indicating uncertainty about their effects on body weight. Additionally, the military component variable shows minimal differences between groups, suggesting that body weight is largely consistent across different service categories.

The intercept serves as the baseline of the model, representing the expected body weight when all predictors are at their reference levels or zero. While this value is not directly interpretable due to the unrealistic scenario of predictors being zero, it provides a starting point for the model. The results emphasize the significance of body composition measurements, while highlighting the need for further refinement in understanding the role of demographic factors.

```{r}
#| label: fig-model-coefficients
#| fig-cap: The 89% credible intervals of each coefficients
#| echo: false
#| warning: false
#| message: false

library(bayesplot)

posterior <- as.matrix(ansur_bayesian_model)

mcmc_areas(
  posterior,
  pars = c("(Intercept)", "heightin", "waist_circumference", "thigh_circumference", "age", "componentArmy Reserve", "componentRegular Army"),
  prob = 0.89, # 89% credible intervals
  prob_outer = 0.95
) +
  ggtitle("Posterior Distributions of Coefficients") +
  xlab("Estimated Effect") +
  theme_classic()

```

@fig-model-coefficients displays the posterior distributions of the coefficients from the Bayesian regression model, with points representing mean estimates and horizontal lines showing credible intervals. The intercept has a highly negative estimate with tight credible intervals, suggesting strong certainty. Waist circumference and thigh circumference have positive effects with narrower credible intervals, indicating more reliable associations with body weight. In contrast, height, age, and component variables (Army Reserve and Regular Army) have wide credible intervals overlapping zero, indicating substantial uncertainty and weak or negligible evidence for their effects.

The Bayesian regression analysis highlights the significant positive associations between body weight and anthropometric predictors, particularly waist circumference and thigh circumference, among female U.S. Army personnel. These findings emphasize the importance of body composition measurements in understanding variations in weight. However, the weak and uncertain effects of height, age, and military component suggest that these factors contribute less reliably to the model, underscoring the complexity of weight determinants. The results reinforce the utility of anthropometric data for health monitoring and fitness interventions, while also identifying areas where further refinement and exploration of additional predictors could enhance the model's explatory power.

# Discussion {#sec-discussion}

This study sought to understand the relationship between body weight and anthropometric and demographic predictors among female U.S. Army personnel through a Bayesian regression framework. By selectively incorporating key variables, such as height, waist circumference, thigh circumference, age, and military component, this analysis identifies patterns that highlight the critical role of body composition measurements in predicting weight while accounting for demographic variability.

## Understanding Anthropometric Contributions

The results emphasize the significance of anthropometric variables, particularly waist circumference and thigh circumference, in predicting body weight. These findings align with established literature, which associates these measurements with fat distribution and muscle mass, critical components of overall body weight. The observed positive associations reinforce the relevance of these variables for health monitoring, fitness interventions, and ergonomic considerations within the military. While height showed weaker effects, its contribution to body weight variability remains biologically plausible, suggesting its inclusion as a baseline predictor in similar analyses.

## Limitations and Future Directions

Despite its contributions, this study is constrained by several limitations. First, the dataset focuses exclusively on female personnel, limiting the generalizability of findings to other populations. Additionally, while anthropometric measurements were comprehensive, other potentially influential variables, such as physical activity levels, dietary habits, or metabolic rates, were not included. Future research could integrate these variables to enhance the explanatory power of predictive models. Expanding the dataset to include male personnel or non-military populations could also provide comparative insights into the determinants of body weight across different contexts.

Moreover, while the Bayesian framework offers robust parameter estimates and credible intervals, incorporating hierarchical models could account for potential dependencies within subgroups (e.g., military components). This approach would allow for a deeper understanding of group-level differences while preserving individual-level variability.

## Broader Implications for Health and Military Readiness

This research highlights the utility of anthropometric measurements for predicting body weight, providing valuable insights for health monitoring, fitness interventions, and equipment design within the military. The findings can inform policies aimed at optimizing physical readiness and reducing injury risks among service members. Furthermore, the approach used in this study demonstrates the potential of Bayesian regression models in health and military research, offering a flexible and interpretable framework for understanding complex relationships among biological and demographic factors.

Looking forward, integrating additional datasets and applying advanced statistical methods, such as machine learning or longitudinal analyses, could provide new insights into the dynamic relationships between body composition, fitness, and operational readiness. By building on the findings of this study, future research can enhance the understanding of weight determinants and contribute to improved health outcomes and performance standards within the military.

\newpage

\appendix

# Appendix {.unnumbered}

# Model details {#sec-model-details}

## Posterior Predictive Check

In @fig-ppcheckandposteriorvsprior-1, we implement a posterior predictive check to assess how well the model predicts the observed data. This plot compares the simulated data from the model’s posterior to the actual observed data, providing insight into the adequacy of the model's fit. A good fit would display overlapping distributions of the predicted and observed values, indicating that the model effectively captures the key characteristics of the data. The posterior predictive check reveals discrepancies between the model's predicted outcomes and the observed data. The central tendency of the model's predictions is centered around 0, with a predicted y intercept of approximately 0.003. In contrast, the actual data exhibits a central tendency around 150, with an observed y intercept closer to 0.02.This mismatch suggests that while the model captures some aspects of the data distribution, it fails to fully align with the observed scale and central tendency.

in @fig-ppcheckandposteriorvsprior-2, we compares the posterior and prior distributions for each parameter in the model. The posterior distributions reflect the data's influence on the estimates, while the prior distributions represent the initial assumptions before observing the data. Parameters such as waist circumference, thigh circumference, and sigma show a noticeable shift from prior to posterior, indicating that the data had a strong influence on these estimates. In contrast, parameters like age and military component remain closer to their prior distributions, reflecting weaker evidence from the data to update these estimates.

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: Examining how the model fits, and is influenced by the data.
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

library(here)

file_path <- here::here("data", "analysis-data", "ansur_female_data.parquet")

# Check if the file exists before attempting to read
if (file.exists(file_path)) {
  sampled_ansur_data <- read_parquet(file_path) %>%
    sample_n(1000)  # Sample 1000 rows
} else {
  stop("File not found: ", file_path)
}
pp_check(ansur_bayesian_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(ansur_bayesian_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()

```

## Diagnostics

@fig-stanareyouokay-1 shows a trace plot, which evaluates the convergence of the MCMC algorithm by examining the sampled values for each parameter across iterations. Each parameter's chain appears to mix well, with no clear trends or patterns over the iterations, indicating stable convergence. The chains overlap consistently, suggesting that the sampling algorithm has explored the posterior distribution effectively. This behavior implies that the Bayesian model's estimates are reliable and not overly sensitive to initial values or random sampling variation.

@fig-stanareyouokay-2 shows the Rhat plot, where values close to 1 indicate convergence for each parameter. All parameters have Rhat values very close to 1.00, well below the threshold of 1.05. This confirms that the chains have converged and the samples are representative of the true posterior distribution.

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: Checking the convergence of the MCMC algorithm
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(ansur_bayesian_model, "trace")

plot(ansur_bayesian_model, "rhat")

```

\newpage

# References

### 2024-11-25 scripts/00-simulate-data.R

@@ -1,0 +1,42 @@
+#### Preamble ####
+# Purpose: Simulates a dataset of anthropometric and demographic data for analysis
+# Author: 
+# Date: 
+# License: MIT
+
+#### Workspace setup ####
+library(tidyverse)
+set.seed(123)  # Set seed for reproducibility
+
+#### Simulate data ####
+
+# Define the number of observations
+n <- 1000
+
+# Simulate data
+simulated_data <- tibble(
+  weight = rnorm(n, mean = 70, sd = 15),                     # Weight in kg (normal distribution)
+  height = rnorm(n, mean = 165, sd = 10),                   # Height in cm
+  waist_circumference = rnorm(n, mean = 85, sd = 15),        # Waist circumference in cm
+  chest_circumference = rnorm(n, mean = 95, sd = 10),        # Chest circumference in cm
+  thigh_circumference = rnorm(n, mean = 55, sd = 7),         # Thigh circumference in cm
+  biceps_circumference = rnorm(n, mean = 30, sd = 5),        # Biceps circumference in cm
+  gender = sample(c("Male", "Female"), size = n, replace = TRUE, prob = c(0.5, 0.5)), # Gender
+  age = sample(18:60, size = n, replace = TRUE),             # Age in years (uniform distribution)
+  ethnicity = sample(
+    c("Asian", "Black", "Hispanic", "White", "Other"),
+    size = n,
+    replace = TRUE,
+    prob = c(0.25, 0.15, 0.2, 0.3, 0.1)                     # Ethnicity probabilities
+  ),
+  component = sample(
+    c("Regular Army", "Reserves", "National Guard"),
+    size = n,
+    replace = TRUE,
+    prob = c(0.6, 0.3, 0.1)                                 # Military component probabilities
+  )
+)
+
+# Display the first few rows of the simulated data
+head(simulated_data)
+

### 2024-11-25 scripts/01-download_data.R

@@ -1,0 +1,24 @@
+#### Preamble ####
+# Purpose: Downloads and saves the data 
+# Author:
+# Date:
+# Contact:
+# License: MIT
+# Pre-requisites: None
+
+
+#### Workspace setup ####
+library(tidyverse)
+library(arrow)
+
+
+#### Download data ####
+ansur_female_data <-
+  read_csv(
+    here::here("data/raw-data/ANSUR_II_FEMALE_Public.csv"),
+    show_col_types = FALSE
+  )
+#### Save data ####
+write_parquet(ansur_female_data, "data/raw-data/ansur_female_data.parquet")
+write_csv(ansur_female_data, "data/raw-data/ansur_female_data.csv")
+

### 2024-11-25 scripts/02-clean_data.R

@@ -1,0 +1,39 @@
+#### Preamble ####
+# Purpose: Cleans the raw ANSUR II Female Dataset for analysis
+# Author: 
+# Date: 
+# License: MIT
+# Pre-requisites: Raw ANSUR II Female data must be available in the specified directory.
+
+#### Workspace setup ####
+library(tidyverse)
+library(janitor) # For clean_names()
+library(tidyr)   # For drop_na()
+
+#### Clean data ####
+# Load the raw data
+raw_data <- read_csv("data/raw-data/ansur_female_data.csv")
+
+# Clean and prepare the data
+cleaned_data <- 
+  raw_data |>
+  janitor::clean_names() |>  # Standardize column names
+  select( weightlbs, heightin, waistcircumference, 
+         thighcircumference, age, component) |>  # Select relevant variables
+  drop_na() |>  # Remove rows with missing values
+  mutate(
+    # Convert character columns to appropriate types if necessary
+    component = as.factor(component),
+    age = as.numeric(age),
+    waistcircumference = waistcircumference / 10,
+    thighcircumference = thighcircumference / 10
+  ) |> 
+  rename(
+    waist_circumference = waistcircumference,
+    thigh_circumference = thighcircumference,
+  )
+
+#### Save data ####
+write_csv(cleaned_data, "data/analysis-data/ansur_female_data.csv")
+write_parquet(cleaned_data, "data/analysis-data/ansur_female_data.parquet")
+

### 2024-11-25 scripts/03-test_analysis.R

@@ -1,0 +1,50 @@
+#### Preamble ####
+# Purpose: Tests the structure and validity of the cleaned ANSUR II Female dataset
+# Author: [Your Name] [...UPDATE THIS...]
+# Date: [Today's Date] [...UPDATE THIS...]
+# Contact: [Your Contact Information] [...UPDATE THIS...]
+# License: MIT
+# Pre-requisites: 
+# - The `tidyverse` and `testthat` packages must be installed and loaded.
+# - 03-clean_data.R must have been run.
+# Any other information needed? Make sure you are in the correct R project directory.
+
+#### Workspace setup ####
+library(tidyverse)
+library(testthat)
+
+analysis_data <- read_csv("data/analysis-data/ansur_female_data.csv")
+
+
+# Test if the data was successfully loaded
+if (exists("analysis_data")) {
+  message("Test Passed: The dataset was successfully loaded.")
+} else {
+  stop("Test Failed: The dataset could not be loaded.")
+}
+
+#### Test data ####
+
+# Test if the dataset has the correct number of columns (10 expected)
+
+# Test if there are any missing values in the dataset
+if (all(!is.na(analysis_data))) {
+  message("Test Passed: The dataset contains no missing values.")
+} else {
+  stop("Test Failed: The dataset contains missing values.")
+}
+
+# Test that `component` column contains at least 2 unique values
+if (length(unique(analysis_data$component)) >= 2) {
+  message("Test Passed: The 'component' column contains at least 2 unique values.")
+} else {
+  stop("Test Failed: The 'component' column does not contain at least 2 unique values.")
+}
+
+# Check for duplicate rows
+if (nrow(analysis_data) == nrow(distinct(analysis_data))) {
+  message("Test Passed: There are no duplicate rows in the dataset.")
+} else {
+  stop("Test Failed: The dataset contains duplicate rows.")
+}
+

### 2024-11-25 paper/Exploring_the_Determinants_of_Body_Weight.qmd
Add files via upload

@@
 
-Body weight is a critical factor influencing physical performance, health, and operational readiness, especially in physically demanding occupations like military service.
-Within the U.S.
-Army, maintaining optimal weight is vital for soldiers to meet physical fitness standards, minimize injury risks, and ensure the success of military operations.
-Furthermore, excessive weight can increase healthcare costs and compromise operational efficiency, underscoring the importance of understanding the factors that contribute to variations in body weight.
-Despite the extensive data collected on anthropometric and demographic characteristics of military personnel, there is limited research examining how these factors collectively influence body weight among U.S.
-Army soldiers, particularly female personnel.
+Body weight significantly influences physical performance, health, and operational readiness in demanding occupations like military service.
+In the U.S.
+Army, maintaining optimal weight is essential for meeting fitness standards, minimizing injury risks, and ensuring operational efficiency.
+Despite the availability of extensive anthropometric and demographic data, limited research examines how these factors collectively impact body weight, particularly among female soldiers [@gordon2014].
 
-This study aims to fill this gap by leveraging the 2012 U.S.
-Army Anthropometric Survey (ANSUR II) Female Dataset, a comprehensive collection of anthropometric and demographic measurements of female Army personnel.
-Specifically, the study focuses on identifying key anthropometric and demographic predictors of body weight and developing a predictive model to enhance health monitoring, fitness interventions, and equipment design.
-By examining relationships between body weight and variables such as height, waist circumference, and demographic factors like age and ethnicity, this research offers new insights into the determinants of body weight in a physically demanding workforce.
+This study addresses this gap using the 2012 U.S.
+Army Anthropometric Survey (ANSUR II) Female Dataset, which includes rigorous anthropometric and demographic measurements of female personnel.
+Data collection employed standardized instruments, such as stadiometers and calipers, ensuring consistency and reliability [@hotzman2011; @paquette2009].
+Variables like height, waist circumference, and thigh circumference were measured to capture body composition, while demographic data such as age, ethnicity, and military component were cross-verified with administrative records [@gordon2014].
 
-Our findings reveal that a combination of anthropometric measurements, including height, waist circumference, and upper and lower body circumferences, significantly predict body weight.
-Demographic factors, such as age and ethnicity, also contribute to variations in weight, highlighting the interplay between biological and environmental factors.
-The predictive model developed in this study demonstrates strong performance, offering practical applications for designing personalized fitness programs, improving health outcomes, and optimizing military gear.
+The analysis highlights anthropometric variables as strong predictors of body weight and demographic factors as additional contributors.
+These findings support personalized fitness programs, improved health outcomes, and optimized military gear for enhancing operational readiness [@opendesignlab2018; @paquette2009].
 
-This paper is organized as follows: Section 2 reviews the methodology, including the selection of variables and statistical approach.
-Section 3 presents the results, focusing on the significance of predictors and model performance.
-Section 4 discusses the implications of the findings for military readiness, health interventions, and equipment design.
-Finally, Section 5 concludes with the study’s contributions, limitations, and suggestions for future research.
+This paper is organized as follows: Section [@sec-intro] provides an overview of the study's background and objectives.
+Section [@sec-data] introduces the dataset and offers an analysis of key variables.
+Section [@sec-model] details the methodology, including the Bayesian regression model employed.
+Section [@sec-result] presents the results, emphasizing the significance of predictors and model performance.
+Section [@sec-discussion] explores the study's limitations and provides directions for future research.
+Lastly, Section [@sec-model-details] presents posterior predictive checks, diagnostic plots, and their interpretations.
 
@@
 
-This study estimates the relationship between body weight and key anthropometric and demographic variables among female U.S.
+This study seeks to estimate the relationship between body weight and a set of key anthropometric and demographic variables among female U.S.
 Army personnel.
-It quantifies how variations in measurements like height and waist circumference, and factors such as age and ethnicity, influence body weight, aiming to identify significant predictors and develop a robust predictive model.
+Specifically, it aims to quantify how variations in anthropometric measurements, such as height and waist circumference, as well as demographic factors, including age and ethnicity, influence body weight.
+The objective is to identify significant predictors and develop a robust predictive model to enhance understanding and practical applications in health monitoring, fitness interventions, and equipment design.
 
@@
 
-The dataset used in this study is the 2012 U.S.
-Army Anthropometric Survey (ANSUR II) Female Dataset, which provides detailed anthropometric and demographic measurements of 1,986 female U.S.
-Army personnel.
-The data collection was conducted by the Natick Soldier Research, Development and Engineering Center (NSRDEC) between 2010 and 2012, using standardized protocols to ensure consistency and reliability.
+Body weight is a crucial determinant of physical performance, health, and operational readiness, particularly in occupations like military service.
+In the U.S.
+Army, maintaining optimal weight is essential for meeting fitness standards, minimizing injury risks, and ensuring operational success.
+However, limited research has explored how anthropometric and demographic factors collectively influence body weight among female soldiers.
 
-Anthropometric measurements were collected using precise tools such as stadiometers, measuring tapes, and calipers, ensuring accurate capture of variables like stature (height in cm), waist circumference, chest circumference, and biceps circumference (flexed).
-For example, stature was measured with participants standing upright, waist circumference at the narrowest point of the torso, and chest circumference at its widest point.
-These methods ensured that the physical measurements reflected real-world body compositions with minimal error.
+This study addresses this gap using the 2012 U.S.
+Army Anthropometric Survey (ANSUR II) Female Dataset [@dacowits2012; @openlab2024].
+The dataset contains anthropometric and demographic measurements for 1,986 female U.S.
+Army personnel, collected by the Natick Soldier Research, Development, and Engineering Center (NSRDEC) using standardized protocols.
+Variables such as stature, waist circumference, and chest circumference were measured with precise instruments, while demographic data like age and military component were cross-verified with administrative records to ensure accuracy [@dacowits2012; @phhealth2024].
 
-Demographic variables, including age, ethnicity, and component (Active Duty, Reserves, or National Guard), were self-reported and cross-verified with administrative records to ensure accuracy.
-This meticulous process ensured that both physical and demographic data were reliable for analysis.
+By examining relationships between body weight and variables like height, waist circumference, age, and military component, this study aims to identify key predictors and develop a robust predictive model.
+The findings offer insights into the determinants of body weight and practical applications for health monitoring, fitness interventions, and military equipment design.
 
-Data preprocessing for this study involved cleaning and organizing the dataset to focus on variables relevant to predicting body weight.
-This included removing implausible outliers, ensuring uniformity in measurement units, and verifying data completeness.
-The clean dataset was analyzed and modeled using R, leveraging the following packages:
+## Data Preprocessing and Tools
 
--   `tidyverse`: For efficient data manipulation and visualization.
+The data for this study was systematically downloaded, cleaned, analyzed, modeled, and visualized using R [@citeR], an extensive statistical programming language.
+The following packages were used for this study:
 
--   `ggplot2`: To create detailed and insightful visualizations.
-
--   `dplyr`: For transforming and summarizing the dataset effectively.
-
--   `broom`: For tidying model outputs and integrating them into analysis workflows.
-
--   `caret`: To support the modeling and evaluation of predictive models.
-
--   `knitr`: For creating dynamic, reproducible reports.
+- **`tidyverse`** [@tidyverse]: To streamline the process of data manipulation and visualization.
+- **`ggplot2`** [@ggplot2]: Used for its powerful and flexible capabilities in creating various types of visualizations tailored to the needs of this study.
+- **`dplyr`** [@dplyr]: Employed for its intuitive functions to transform and summarize complex datasets effectively.
+- **`broom`** [@broom]: Used to tidy up model outputs and seamlessly integrate them into the analysis workflow.
+- **`rstanarm`** [@rstanarm]: Facilitated the implementation of Bayesian models, providing a straightforward way to fit regression models using Stan.
+- **`bayesplot`** [@bayesplot]: Utilized for creating graphical posterior predictive checks and diagnostic plots to assess model fit.
+- **`arrow`** [@arrow]: Used for efficiently reading and writing large datasets, enhancing data handling capabilities.
+- **`tinytable`** [@tinytable]: Used to create compact and well-organized summary tables for presenting data and model outputs effectively.
+- **`modelsummary`** [@modelsummary]: Used for creating professional-quality regression tables and visualizations to summarize model results clearly.
+- **`knitr`** [@knitr]: Employed to dynamically generate reproducible reports that integrate R code with its outputs, allowing for seamless inclusion of plots and analysis results in the final document.
+- **_Telling Stories with Data_** [@tellingstories]: This book was consulted for its statistical information.
 
@@
 
-#### Body Weight in Pounds {#sec-body-weight}
+### Body Weight in Pounds {#sec-body-weight}
 
-The outcome variable for this study is weightlbs, which measures the body weight of female U.S.
-Army personnel in pounds.
-This variable represents the total body mass of an individual and serves as the dependent variable in the analysis.
-Understanding variations in body weight is crucial for examining physical readiness, health risks, and the design of military equipment tailored to individual needs.
+The outcome variable for this study is weightlbs, which represents the body weight of female U.S.
+Army personnel, measured in pounds.
+This variable serves as the dependent variable in the analysis and reflects the total body mass of each individual.
+Understanding variations in body weight is essential for assessing physical readiness, identifying health risks, and optimizing the design of military equipment to meet individual needs.
 
-\@fig-weight-distribution illustrates the distribution of body weight among the sample population.
-The histogram shows that most individuals weigh between 120 lbs and 160 lbs, with the distribution displaying a slight right skew.
-This skew indicates the presence of a few individuals with higher body weights, though these are relatively uncommon.
+[@fig-weight-distribution] illustrates the distribution of body weight within the sample population.
+The histogram reveals that the majority of individuals weigh between 120 lbs and 160 lbs, with the distribution displaying a slight right skew.
+This skew suggests the presence of a small number of individuals with higher body weights, though such cases are relatively infrequent.
 
@@
 
-#### Height {#sec-height}
+### Height {#sec-height}
 
-Height, measured as heightin in inches, is one of the primary predictors of body weight.
-Taller individuals typically have larger skeletal structures and more body mass, making height a critical variable in understanding variations in weight.
+Height, recorded as heightin in inches, is a key predictor of body weight.
+Taller individuals generally possess larger skeletal structures and greater body mass, making height a crucial variable for understanding variations in weight among the sample population.
 
-\@fig-height-distribution shows the distribution of height among the sample population.
-Most individuals have heights clustered between 58 inches and 71 inches, with a central tendency around 63 inches.
-The distribution appears approximately normal if despite the outliers of person above 73 inches, which aligns with expected variations in height for adult females.
+[@fig-height-distribution] illustrates the distribution of height within the dataset.
+The majority of individuals have heights ranging from 58 inches to 71 inches, with a central tendency around 63 inches.
+The distribution is approximately normal, despite a few outliers exceeding 73 inches.
+These outliers align with the natural variation in height observed among adult females.
 
@@
 
-#### Waist Circumference {#sec-waist-circumference}
+### Waist Circumference {#sec-waist-circumference}
 
 Waist circumference is a key anthropometric variable that reflects abdominal fat distribution and overall body composition.
-In this dataset, waist_circumference was measured at the narrowest part of the torso using a flexible measuring tape, ensuring accuracy and consistency.
+In this dataset, waist_circumference was measured at the narrowest part of the torso using a flexible measuring tape, ensuring both accuracy and consistency.
 
 Waist circumference is a strong predictor of body weight due to its association with abdominal fat and overall body mass.
-This variable is expected to show a moderate to strong positive correlation with weight, particularly as it reflects adiposity and central body composition.
+This variable is expected to exhibit a moderate to strong positive correlation with weight, as it effectively reflects central adiposity and overall body composition.
 
-@fig-waist-thigh-violin-plots The violin plot shows that most values are concentrated between approximately 65 cm and 90 cm, with a central tendency around the mid-point of this range.
-Outliers are present above 115 cm, indicating a small number of individuals with unusually large waist circumferences.
-The overall spread (interquartile range) is moderate.
+[@fig-waist-thigh-violin-plots] displays the distribution of waist circumference.
+Most values are concentrated between approximately 65 cm and 90 cm, with a central tendency around the mid-point of this range.
+Outliers above 115 cm represent a small subset of individuals with unusually large waist circumferences.
+The overall spread, as indicated by the interquartile range, is moderate.
 
-#### Thigh Circumference {#sec-thigh-circumference}
+### Thigh Circumference {#sec-thigh-circumference}
 
-Thigh circumference measures the size of the upper leg, reflecting both muscle mass and fat distribution in the lower body.
-In this dataset, thigh_circumference was measured at the largest part of the thigh using a flexible measuring tape, ensuring consistency.
+Thigh circumference measures the size of the upper leg and reflects both muscle mass and fat distribution in the lower body.
+In this dataset, thigh_circumference was measured at the largest part of the thigh using a flexible measuring tape to ensure consistency.
 
-@fig-waist-thigh-violin-plots shows the distribution is slightly narrower than that of waist circumference, with most values falling between 50 cm and 65 cm, The median appears to be around 61 cm.
-A few outliers exist above 75 cm, representing individuals with larger thigh circumferences.
+As shown in [@fig-waist-thigh-violin-plots], the distribution of thigh circumference is slightly narrower compared to that of waist circumference.
+Most values fall between 50 cm and 65 cm, with a median around 61 cm.
+A few outliers exceed 75 cm, representing individuals with larger thigh circumferences.
 
-Thigh circumference provides insight into lower body muscle and fat distribution, making it an important predictor of weight.
-This variable is expected to have a positive correlation with body weight, as larger thigh circumferences typically indicate greater body mass.
+Thigh circumference provides valuable insights into lower body muscle and fat distribution, making it an important predictor of body weight.
+This variable is expected to positively correlate with body weight, as larger thigh circumferences typically indicate greater overall body mass.
 
@@
 
-#### Age {#sec-age}
+### Age {#sec-age}
 
-Age is a critical demographic variable in this study, reflecting biological and lifestyle factors that influence body weight.
-As individuals age, changes in metabolism, muscle mass, and fat distribution can impact body composition.
-In the dataset, age is measured in years and was self-reported by participants, with additional verification through administrative records to ensure accuracy.
+Age is a crucial demographic variable in this study, as it encapsulates biological and lifestyle factors that influence body weight.
+Variations in metabolism, muscle mass, and fat distribution associated with aging play a significant role in shaping body composition.
+In this dataset, age is measured in years and was self-reported by participants, with additional verification through administrative records to ensure accuracy.
 
-@tbl-age-distribution illustrates the distribution of age within the sample population. Most individuals are between 22 and 34 years old, with a noticeable peak around the late 20s.
+[@tbl-age-distribution] presents the distribution of age within the sample population.
+The majority of individuals are between 22 and 34 years old, with a pronounced peak observed in the late 20s.
+This age range reflects the demographic composition of the sample and provides a foundation for analyzing age-related influences on body weight.
 
@@
 
-#### Component {#sec-component}
+### Component {#sec-component}
 
-Component refers to the military branch or service type (e.g., Active Duty, Reserves, or National Guard) of the female U.S.
+The component variable refers to the military branch or service type (e.g., Active Duty, Reserves, or National Guard) of the female U.S.
 Army personnel.
-This demographic variable is categorical and provides insight into lifestyle and activity differences that may influence body weight.
-For instance, Active Duty personnel may have different physical fitness levels compared to those in the Reserves or National Guard due to varying levels of daily activity and training regimens.
+This categorical demographic variable provides valuable insights into lifestyle and activity differences that may influence body weight.
+For example, Active Duty personnel often exhibit higher physical fitness levels compared to those in the Reserves or National Guard due to differences in daily activity and training regimens.
 
-\@tbl-component-distribution shows the distribution of military components among female U.S.
+[@tbl-component-distribution] presents the distribution of military components among female U.S.
 Army personnel, categorized as Regular Army, Army Reserve, and National Guard.
-The Regular Army comprises the majority (51.36%, 1,020 individuals), reflecting high physical activity levels due to daily duties and training.
-The National Guard represents 42.65% (847 individuals), with more variable schedules balancing civilian and military roles.
-The Army Reserve, the smallest group (5.99%, 119 individuals), likely experiences intermittent physical activity due to less frequent training requirements.
+The Regular Army constitutes the majority of the sample (51.36%, 1,020 individuals), reflecting high physical activity levels associated with daily duties and training.
+The National Guard accounts for 42.65% of the sample (847 individuals), representing individuals who balance civilian and military responsibilities with variable activity levels.
+The Army Reserve, comprising the smallest group (5.99%, 119 individuals), likely experiences lower and intermittent physical activity due to less frequent training requirements.
 
@@
 
-# Model
+# Model {#sec-model}
 
@@
 
-To analyze the relationship between body weight and selected predictors, a Bayesian regression model was constructed using the cleaned ANSUR II Female data.
-The Bayesian regression model uses a Gaussian likelihood function.
-The model is based on a total of 1000 observations, randomly sampled from the cleaned dataset.
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm, taking advantage of its efficient Bayesian estimation techniques for continuous outcome variables.
-The model uses weight (kg) as the dependent variable and the following predictors:
+A Bayesian regression model was constructed to analyze the relationship between body weight and selected predictors using the cleaned ANSUR II Female Dataset.
+The model employs a Gaussian likelihood function and was estimated using 1,000 observations randomly sampled from the dataset.
+The analysis was conducted in R [@citeR], utilizing the rstanarm package [@rstanarm], which provides efficient Bayesian estimation techniques for continuous outcome variables.
+The dependent variable is body weight (in kilograms), and the following predictors were included:
 
@@
 
-$\eta_i = \beta_0 + \beta_1 \cdot \text{height}_i + \beta_2 \cdot \text{waist circumference}_i + \beta_3 \cdot \text{thigh circumference}_i + \beta_4 \cdot \text{age}_i + \beta_5 \cdot \text{component}_i$​
+$\eta_i = \beta_0 + \beta_1 \cdot \text{height}_i + \beta_2 \cdot \text{waist circumference}_i + \beta_3 \cdot \text{thigh circumference}_i + \beta_4 \cdot \text{age}_i + \beta_5 \cdot \text{component}_i$
 
@@
 
-In the Bayesian regression model implemented using the rstanarm package, default priors are applied to the model parameters to ensure robust and reliable inference.
-These priors are designed to be weakly informative, balancing the need for regularization with flexibility to adapt to the data:
+The Bayesian regression model utilizes default priors provided by the rstanarm package, ensuring robust and reliable inference.
+These priors are weakly informative, balancing regularization with the flexibility to adapt to the data:
 
@@
 
-The priors are intentionally weakly informative to provide flexibility while maintaining some level of regularization, ensuring that the model remains robust to overfitting.
-The rstanarm package handles the specification and implementation of these priors, making Bayesian inference accessible for a wide range of applications.
-By incorporating these priors, the model can better capture the relationships between predictors and body weight, producing credible parameter estimates and uncertainty quantification.
+The weakly informative priors are designed to enhance the model’s robustness, ensuring credible parameter estimates and reliable uncertainty quantification.
+The use of Bayesian priors provides an added layer of rigor, particularly when estimating complex relationships between predictors and body weight.
+The rstanarm package facilitates the implementation of these priors, making Bayesian inference accessible and effective for this analysis.
 
-# Results
+# Results {#sec-result}
 
@@
 
-The Bayesian regression model was developed to understand the relationship between body weight and anthropometric and demographic predictors among female U.S.
+The Bayesian regression model was developed to investigate the relationship between body weight and key anthropometric and demographic predictors among female U.S.
 Army personnel.
 The predictors included height, waist circumference, thigh circumference, age, and military component.
-The analysis revealed that anthropometric measurements, particularly height, waist circumference, and thigh circumference, have significant positive associations with body weight, while age and component showed smaller but meaningful effects.
-These findings are summarized in @tbl-bayesian-model-summary.
+The analysis identified significant positive associations between body weight and the anthropometric predictors—height, waist circumference, and thigh circumference—highlighting their strong influence on body weight.
+Age and military component demonstrated smaller but meaningful effects, reflecting their nuanced contributions to variations in body weight.
+A summary of these findings is presented in [@tbl-bayesian-model-summary].
 
@@
 
-The coefficient summary presented in @tbl-bayesian-model-summary reflects the relationships between body weight and selected predictors among female U.S.
+The coefficient summary presented in [@tbl-bayesian-model-summary] highlights the relationships between body weight and the selected predictors among female U.S.
 Army personnel.
-For instance, waist circumference and thigh circumference show positive mean coefficients, suggesting their roles as key indicators of body weight, with increases in these measurements associated with higher body weight.
-These findings align with the expected relationship between anthropometric dimensions and overall body mass.
+Anthropometric variables, particularly waist circumference and thigh circumference, show positive mean coefficients, underscoring their roles as key indicators of body weight.
+Increases in these measurements are associated with higher body weight, which aligns with established relationships between body dimensions and overall mass.
 
-Conversely, the coefficients for age and height exhibit weak associations, with credible intervals that include zero, indicating uncertainty about their effects on body weight.
-Additionally, the military component variable shows minimal differences between groups, suggesting that body weight is largely consistent across different service categories.
+In contrast, the coefficients for age and height exhibit weak associations, with credible intervals that include zero, indicating uncertainty about their effects on body weight.
+Similarly, the military component variable shows minimal differences between service categories, suggesting that body weight is largely consistent across Active Duty, Reserves, and National Guard personnel.
 
-The intercept serves as the baseline of the model, representing the expected body weight when all predictors are at their reference levels or zero.
-While this value is not directly interpretable due to the unrealistic scenario of predictors being zero, it provides a starting point for the model.
-The results emphasize the significance of body composition measurements, while highlighting the need for further refinement in understanding the role of demographic factors.
+The model’s intercept represents the baseline body weight when all predictors are at their reference levels or zero.
+While this value lacks direct interpretability due to the unrealistic scenario of zero predictors, it provides a conceptual starting point for the model.
+These findings emphasize the importance of anthropometric measurements in predicting body weight while underscoring the need for further exploration of demographic factors to refine the model.
 
@@
 
-@fig-model-coefficients displays the posterior distributions of the coefficients from the Bayesian regression model, with points representing mean estimates and horizontal lines showing credible intervals.
-The intercept has a highly negative estimate with tight credible intervals, suggesting strong certainty.
-Waist circumference and thigh circumference have positive effects with narrower credible intervals, indicating more reliable associations with body weight.
-In contrast, height, age, and component variables (Army Reserve and Regular Army) have wide credible intervals overlapping zero, indicating substantial uncertainty and weak or negligible evidence for their effects.
+[@fig-model-coefficients] illustrates the posterior distributions of the coefficients from the Bayesian regression model.
+Points represent the mean estimates, while horizontal lines indicate the credible intervals.
+The intercept has a strongly negative estimate with narrow credible intervals, reflecting high certainty in its value.
+Waist circumference and thigh circumference demonstrate positive effects with relatively narrow credible intervals, indicating reliable and significant associations with body weight.
+In contrast, height, age, and the military component variables (Army Reserve and Regular Army) exhibit wide credible intervals overlapping zero, suggesting substantial uncertainty and weak or negligible evidence for their effects.
 
-The Bayesian regression analysis highlights the significant positive associations between body weight and anthropometric predictors, particularly waist circumference and thigh circumference, among female U.S.
+The Bayesian regression analysis underscores the significant positive associations between body weight and anthropometric predictors, particularly waist circumference and thigh circumference, among female U.S.
 Army personnel.
-These findings emphasize the importance of body composition measurements in understanding variations in weight.
-However, the weak and uncertain effects of height, age, and military component suggest that these factors contribute less reliably to the model, underscoring the complexity of weight determinants.
-The results reinforce the utility of anthropometric data for health monitoring and fitness interventions, while also identifying areas where further refinement and exploration of additional predictors could enhance the model's explatory power.
+These findings highlight the critical role of body composition measurements in explaining variations in body weight.
+Conversely, the uncertain effects of height, age, and military component suggest that these factors contribute less reliably to the model, reflecting the multifaceted nature of weight determinants.
+These results affirm the utility of anthropometric data in health monitoring and fitness interventions while identifying areas for further refinement.
+Exploring additional predictors may enhance the model’s explanatory power and improve its utility in practical applications.
 
@@
 
-This study sought to understand the relationship between body weight and anthropometric and demographic predictors among female U.S.
-Army personnel through a Bayesian regression framework.
-By selectively incorporating key variables, such as height, waist circumference, thigh circumference, age, and military component, this analysis identifies patterns that highlight the critical role of body composition measurements in predicting weight while accounting for demographic variability.
+This study aimed to investigate the relationship between body weight and key anthropometric and demographic predictors among female U.S.
+Army personnel using a Bayesian regression framework.
+By incorporating variables such as height, waist circumference, thigh circumference, age, and military component, the analysis highlights the critical role of body composition measurements in predicting body weight while accounting for demographic variability.
 
@@
 
-The results emphasize the significance of anthropometric variables, particularly waist circumference and thigh circumference, in predicting body weight.
-These findings align with established literature, which associates these measurements with fat distribution and muscle mass, critical components of overall body weight.
-The observed positive associations reinforce the relevance of these variables for health monitoring, fitness interventions, and ergonomic considerations within the military.
-While height showed weaker effects, its contribution to body weight variability remains biologically plausible, suggesting its inclusion as a baseline predictor in similar analyses.
+The findings underscore the significance of anthropometric variables, particularly waist circumference and thigh circumference, as strong predictors of body weight.
+These results align with established research linking these measurements to fat distribution and muscle mass, which are key determinants of overall body weight.
+The observed positive associations reinforce the importance of these variables in health monitoring, fitness interventions, and ergonomic considerations within the military.
+While the effect of height was weaker, its inclusion as a baseline predictor remains biologically plausible and relevant for analyses of body weight variability.
 
@@
 
-Despite its contributions, this study is constrained by several limitations.
-First, the dataset focuses exclusively on female personnel, limiting the generalizability of findings to other populations.
-Additionally, while anthropometric measurements were comprehensive, other potentially influential variables, such as physical activity levels, dietary habits, or metabolic rates, were not included.
-Future research could integrate these variables to enhance the explanatory power of predictive models.
-Expanding the dataset to include male personnel or non-military populations could also provide comparative insights into the determinants of body weight across different contexts.
+Despite its contributions, this study is subject to several limitations.
+First, the dataset focuses exclusively on female personnel, limiting the generalizability of findings to other populations, including male service members or civilians.
+Second, while the dataset includes comprehensive anthropometric measurements, it lacks potentially influential variables such as physical activity levels, dietary habits, and metabolic rates.
+Incorporating these factors in future research could enhance the explanatory power and predictive accuracy of the model.
 
-Moreover, while the Bayesian framework offers robust parameter estimates and credible intervals, incorporating hierarchical models could account for potential dependencies within subgroups (e.g., military components).
-This approach would allow for a deeper understanding of group-level differences while preserving individual-level variability.
+Additionally, while the Bayesian framework provides robust parameter estimates and credible intervals, future studies could benefit from hierarchical modeling to account for dependencies within subgroups, such as different military components.
+This approach would provide a more nuanced understanding of group-level differences while preserving individual-level variability.
+
+Expanding the scope of the dataset to include male personnel or non-military populations could enable comparative analyses and broaden the applicability of the findings.
+Future research should also explore integrating additional datasets and leveraging advanced statistical methods, such as machine learning or longitudinal analyses, to uncover dynamic relationships between body composition, fitness, and operational readiness.
 
@@
 
-This research highlights the utility of anthropometric measurements for predicting body weight, providing valuable insights for health monitoring, fitness interventions, and equipment design within the military.
-The findings can inform policies aimed at optimizing physical readiness and reducing injury risks among service members.
-Furthermore, the approach used in this study demonstrates the potential of Bayesian regression models in health and military research, offering a flexible and interpretable framework for understanding complex relationships among biological and demographic factors.
+This research underscores the utility of anthropometric measurements for predicting body weight, offering valuable insights into health monitoring, fitness interventions, and equipment design within the military.
+The findings can inform policies aimed at enhancing physical readiness and reducing injury risks among service members.
+The use of Bayesian regression models in this study further demonstrates the flexibility and interpretability of these methods for investigating complex relationships among biological and demographic factors.
 
-Looking forward, integrating additional datasets and applying advanced statistical methods, such as machine learning or longitudinal analyses, could provide new insights into the dynamic relationships between body composition, fitness, and operational readiness.
-By building on the findings of this study, future research can enhance the understanding of weight determinants and contribute to improved health outcomes and performance standards within the military.
+Looking forward, integrating more comprehensive datasets and applying advanced analytical techniques could provide deeper insights into the determinants of body weight.
+Such efforts would contribute to a better understanding of how body composition, physical fitness, and operational readiness interact over time.
+Building on the findings of this study, future research can enhance health outcomes, refine performance standards, and ultimately improve the well-being and effectiveness of military personnel.
 
@@
 
-In @fig-ppcheckandposteriorvsprior-1, we implement a posterior predictive check to assess how well the model predicts the observed data.
-This plot compares the simulated data from the model’s posterior to the actual observed data, providing insight into the adequacy of the model's fit.
-A good fit would display overlapping distributions of the predicted and observed values, indicating that the model effectively captures the key characteristics of the data.
-The posterior predictive check reveals discrepancies between the model's predicted outcomes and the observed data.
-The central tendency of the model's predictions is centered around 0, with a predicted y intercept of approximately 0.003.
-In contrast, the actual data exhibits a central tendency around 150, with an observed y intercept closer to 0.02.This mismatch suggests that while the model captures some aspects of the data distribution, it fails to fully align with the observed scale and central tendency.
+[@fig-ppcheckandposteriorvsprior-1] presents a posterior predictive check to evaluate how well the model predicts the observed data.
+This diagnostic compares the simulated data from the model’s posterior distribution with the actual observed data, providing insights into the model's adequacy.
+A good fit is characterized by overlapping distributions of predicted and observed values, indicating that the model effectively captures key characteristics of the data.
 
-in @fig-ppcheckandposteriorvsprior-2, we compares the posterior and prior distributions for each parameter in the model.
-The posterior distributions reflect the data's influence on the estimates, while the prior distributions represent the initial assumptions before observing the data.
-Parameters such as waist circumference, thigh circumference, and sigma show a noticeable shift from prior to posterior, indicating that the data had a strong influence on these estimates.
-In contrast, parameters like age and military component remain closer to their prior distributions, reflecting weaker evidence from the data to update these estimates.
+The posterior predictive check reveals discrepancies between the model's predictions and the observed data.
+The central tendency of the model's predictions is centered around 0, with a predicted yy-intercept of approximately 0.003.
+In contrast, the actual data shows a central tendency around 150, with an observed yy-intercept closer to 0.02.
+This mismatch suggests that while the model captures some aspects of the data distribution, it fails to fully align with the observed scale and central tendency, indicating potential areas for model refinement.
+
+[@fig-ppcheckandposteriorvsprior-2] compares the posterior and prior distributions for each parameter in the model.
+The posterior distributions illustrate the influence of the data on parameter estimates, while the prior distributions represent the initial assumptions before incorporating the observed data.
+
+Notably, parameters such as waist circumference, thigh circumference, and sigma exhibit a significant shift from prior to posterior distributions, indicating that the data strongly informed these estimates.
+In contrast, parameters like age and military component remain closer to their prior distributions, suggesting weaker evidence from the data to update these estimates.
+These patterns highlight the varying levels of influence that the data exert on different parameters and underscore the need to consider additional predictors or alternative modeling approaches to improve the model's explanatory power.
 
@@
 
-@fig-stanareyouokay-1 shows a trace plot, which evaluates the convergence of the MCMC algorithm by examining the sampled values for each parameter across iterations.
-Each parameter's chain appears to mix well, with no clear trends or patterns over the iterations, indicating stable convergence.
-The chains overlap consistently, suggesting that the sampling algorithm has explored the posterior distribution effectively.
-This behavior implies that the Bayesian model's estimates are reliable and not overly sensitive to initial values or random sampling variation.
+[@fig-stanareyouokay-1] presents a trace plot, which assesses the convergence of the Markov Chain Monte Carlo (MCMC) algorithm by examining the sampled values for each parameter across iterations.
+The chains for each parameter exhibit good mixing, with no discernible trends or patterns over the iterations.
+The consistent overlap of chains indicates that the sampling algorithm has effectively explored the posterior distribution.
+These results suggest that the Bayesian model’s estimates are reliable and not overly sensitive to initial values or random sampling variation.
 
-@fig-stanareyouokay-2 shows the Rhat plot, where values close to 1 indicate convergence for each parameter.
-All parameters have Rhat values very close to 1.00, well below the threshold of 1.05.
-This confirms that the chains have converged and the samples are representative of the true posterior distribution.
+[@fig-stanareyouokay-2] displays the Rhat plot, where values close to 1 indicate convergence for each parameter.
+All parameters have Rhat values near 1.00, well below the threshold of 1.05.
+This confirms that the chains have successfully converged and the samples accurately represent the true posterior distribution.
 

### 2024-11-28 paper/Exploring_the_Determinants_of_Body_Weight.qmd
Add files via upload

@@
 title: "Exploring the Determinants of Body Weight: A Bayesian Analysis of Anthropometric and Demographic Factors Among Female U.S. Army Personnel"
-subtitle: "Identifying Key Predictors to Enhance Health Monitoring and Operational Readiness"
+subtitle: "A Bayesian Approach to Identifying Anthropometric and Demographic Predictors of Body Weight in Female U.S. Army Personnel for Improved Health Monitoring and Operational Readiness"
 author: 
-  - aa
-thanks: "Code and data are available at: "
+  - Huayan Yu
+thanks: "Code and data are available at: https://github.com/huayan1998/Exploring_the_Determinants_of_Body_Weight"
 date: today
@@
 This study addresses this gap using the 2012 U.S.
-Army Anthropometric Survey (ANSUR II) Female Dataset [@dacowits2012; @openlab2024].
+Army Anthropometric Survey (ANSUR II) Female Dataset.
 The dataset contains anthropometric and demographic measurements for 1,986 female U.S.
 Army personnel, collected by the Natick Soldier Research, Development, and Engineering Center (NSRDEC) using standardized protocols.
-Variables such as stature, waist circumference, and chest circumference were measured with precise instruments, while demographic data like age and military component were cross-verified with administrative records to ensure accuracy [@dacowits2012; @phhealth2024].
+Variables such as stature, waist circumference, and chest circumference were measured with precise instruments, while demographic data like age and military component were cross-verified with administrative records to ensure accuracy.
 
@@
 - **`dplyr`** [@dplyr]: Employed for its intuitive functions to transform and summarize complex datasets effectively.
-- **`broom`** [@broom]: Used to tidy up model outputs and seamlessly integrate them into the analysis workflow.
 - **`rstanarm`** [@rstanarm]: Facilitated the implementation of Bayesian models, providing a straightforward way to fit regression models using Stan.
@@
 - **`knitr`** [@knitr]: Employed to dynamically generate reproducible reports that integrate R code with its outputs, allowing for seamless inclusion of plots and analysis results in the final document.
+- **`janitor`** [@janitor]: Used for its efficient data cleaning functions, simplifying the process of preprocessing dirty data into a clean, analysis-ready format.
 - **_Telling Stories with Data_** [@tellingstories]: This book was consulted for its statistical information.
@@
 #| label: tbl-head-data
-#| tbl-cap: Table of first 6 rows of the cleaned dataset
+#| tbl-cap: First 6 rows of the cleaned dataset
 #| echo: false
@@
 #| label: fig-waist-thigh-violin-plots
-#| fig-cap: "Figure: Violin plots showing the distribution of waist and thigh circumferences, with individual data points overlaid to provide a detailed visualization of the data spread."
+#| fig-cap: "Violin plots showing the distribution of waist and thigh circumferences, with individual data points overlaid to provide a detailed visualization of the data spread."
 #| echo: false
@@
   labs(
-    title = "Distribution of Waist and Thigh Circumference",
     x = "Measurement",
-    y = "Circumference (in mm)",
+    y = "Circumference (in cm)",
     fill = "Measurement"
@@
 #| label: tbl-age-distribution
-#| tbl-cap: The table showing distribution of age among female U.S. Army personnel, with most individuals between 22 and 34 years old.
+#| tbl-cap: Distribution of age among female U.S. Army personnel, with most individuals between 22 and 34 years old.
 #| echo: false
@@
 
-cap <- "Summary of Age Distribution"
-not <- "The table showing distribution of age among female U.S. Army personnel, with most individuals between 22 and 34 years old."
 # Convert summary to a tinytable
-age_table <- tt(age_summary, caption = cap, notes = not)
+age_table <- tt(age_summary)
 
@@
 #| label: tbl-component-distribution
-#| tbl-cap: The table showing the distribution of military components (Regular Army, Reserves, National Guard) among female U.S. Army personnel.
+#| tbl-cap: Distribution of military components among female U.S. Army personnel.
 #| echo: false
@@
 # Convert to tinytable
-cap <- "Summary of components Distribution"
-not <- 'Distribution of military components are categorized as Regular Army, Reserves, and National Guard.'
-component_table <- tt(component_summary, caption = cap, notes = not)
+component_table <- tt(component_summary)
 
@@
 -   Intercept Priors: For the model’s intercept $\beta_0$, a normal prior distribution is used with a mean of 0 and a standard deviation of 1.
-This prior helps stabilize the intercept estimate without imposing overly strong assumptions about its central value.
+This choice reflects the assumption that the baseline body weight (when all predictors are zero) is centered near the observed scale of the outcome variable but avoids imposing overly strong constraints.
+The standard deviation of 1 allows for reasonable variation, ensuring the prior does not dominate the posterior estimates.
+Given the scale of the predictors (e.g., height, waist circumference), this weakly informative prior stabilizes the intercept estimate without introducing bias.
 
@@
 The rstanarm package facilitates the implementation of these priors, making Bayesian inference accessible and effective for this analysis.
+
+## Justification for the Priors and Model Choice
+
+The choice of weakly informative priors reflects the exploratory nature of this study, where the goal is to identify significant predictors of body weight without imposing strong assumptions on the parameter estimates.
+Normal priors centered around zero with a moderate variance ensure that the model is flexible enough to incorporate data-driven insights while avoiding overfitting.
+This is particularly important given the diversity of predictors, which include anthropometric variables (e.g., waist and thigh circumference) and categorical demographic factors (e.g., military component).
+The priors help balance the varying scales of these predictors, ensuring interpretability and stability in the posterior estimates.
+
+The Bayesian regression framework was chosen for its ability to provide probabilistic estimates, which are particularly useful in quantifying uncertainty and generating credible intervals for the coefficients.
+This approach is well-suited to the study’s context, where understanding the relative influence of anthropometric and demographic predictors on body weight requires a robust and interpretable model.
+The rstanarm package was selected for its efficient handling of Bayesian inference and its built-in diagnostics, allowing for rigorous validation of the model.
+The use of a Gaussian likelihood function aligns with the continuous nature of the outcome variable (body weight), and the model’s structure avoids unnecessary complexity while accurately capturing key relationships in the data.
 
@@
 #| label: tbl-bayesian-model-summary
-#| tbl-cap: Bayesian Regression Model Results.
+#| tbl-cap: Bayesian Regression Model Results
 #| echo: false
@@
 
-# Model details {#sec-model-details}
+# Data Cleaning
+
+The raw ANSUR II Female Dataset was systematically cleaned and prepared for analysis to ensure consistency, accuracy, and relevance of the variables.
+First, the raw dataset was loaded using the read_csv function and processed with the janitor::clean_names() function to standardize column names, making them easier to interpret and work with.
+Key variables relevant to the study—such as weight (weightlbs), height (heightin), waist circumference, thigh circumference, age, and military component—were selected using the select() function to focus the analysis on predictors of interest.
+
+Rows with missing values were removed using drop_na() to maintain data integrity and ensure a complete dataset for modeling.
+Several transformations were applied: character columns like the military component were converted to factors, and the age column was explicitly coerced to numeric to prevent data type inconsistencies.
+Additionally, waist circumference and thigh circumference values were divided by 10 to standardize the unit of measurement (converting millimeters to centimeters), and columns were renamed for clarity.
+Finally, the cleaned dataset was saved in both CSV and Parquet formats for accessibility and compatibility with various analytical tools.
+These steps ensured a clean, well-structured dataset, ready for reliable and reproducible analysis.
+
+# Model Details {#sec-model-details}
 
@@
 
+# Ideal Data Sampling Methodology
+
+In an ideal scenario, the data for this study would be collected using a stratified random sampling method to ensure the sample accurately represents the diverse population of female U.S.
+Army personnel.
+This approach would involve dividing the population into distinct strata based on key demographic and occupational characteristics, such as military component (Active Duty, Reserves, National Guard), age groups (e.g., 18–25, 26–35, 36+ years), and ethnic backgrounds.
+Each stratum would then be sampled independently, with participants randomly selected within each group in proportion to their representation in the overall population.
+Stratified random sampling is particularly effective for heterogeneous populations, as it minimizes sampling bias and ensures that smaller subgroups, such as Reserve personnel or older age groups, are adequately represented.
+
+To implement this method, a comprehensive roster of all female U.S.
+Army personnel would be required.
+This roster would include essential demographic and occupational information to accurately classify individuals into strata.
+Once stratification is complete, participants would be selected using randomization techniques, such as computer-generated random numbers, to eliminate selection bias.
+For instance, if 50% of the total population comprises Active Duty personnel, 50% of the sampled participants would also be drawn from this stratum.
+Similarly, if 20% of personnel fall within the 18–25 age group, this age group would constitute 20% of the sample.
+This proportional allocation ensures that the sample mirrors the characteristics of the entire population.
+
+To enhance the validity and reliability of the data, standardized measurement protocols would be employed during data collection.
+Anthropometric measurements, such as weight, height, waist circumference, and thigh circumference, would be conducted using calibrated instruments and performed by trained professionals to reduce variability.
+Demographic data, such as age, ethnicity, and military component, would be collected through self-reports and cross-verified with official administrative records to ensure accuracy and consistency.
+
+# Ideal Survey Questionnaire
+
+## Section 1: Demographic Information
+1. **What is your age?** (Open-ended)  
+   Example answer: 25
+
+2. **Which military component are you currently serving in?** (Multiple-choice)  
+   - Regular Army  
+   - Army Reserve  
+   - National Guard
+
+3. **What is your ethnic background?** (Multiple-choice)  
+   - White  
+   - Black or African American  
+   - Asian  
+   - Hispanic or Latino  
+   - Native American or Alaska Native  
+   - Native Hawaiian or Pacific Islander  
+   - Other (please specify): ___________
+
+## Section 2: Anthropometric Measurements
+*(Instructions: Please provide accurate measurements. Measurements should be taken by a trained professional or using calibrated equipment.)*
+
+4. **What is your body weight in pounds?** (Open-ended)  
+   Example answer: 142
+
+5. **What is your height in inches?** (Open-ended)  
+   Example answer: 64
+
+6. **What is your waist circumference in centimeters?** (Open-ended)  
+   Example answer: 85.0
+
+7. **What is your thigh circumference in centimeters?** (Open-ended)  
+   Example answer: 62.2
+
+## Section 3: Additional Information
+8. **Do you have any medical conditions that may affect body weight (e.g., metabolic disorders)?** (Multiple-choice)  
+   - Yes (please specify): ___________  
+   - No
+
+9. **How frequently do you engage in physical training as part of your military duties?** (Multiple-choice)  
+   - Daily  
+   - 3-5 times a week  
+   - 1-2 times a week  
+   - Rarely
+
+10. **Do you follow any specific dietary practices or restrictions?** (Multiple-choice)  
+    - Yes (please specify): ___________  
+    - No
+
 \newpage

### 2024-11-28 scripts/00-simulate-data.R
Add files via upload

@@ -6,6 +6,7 @@
 
 #### Workspace setup ####
 library(tidyverse)
+library(arrow)
 set.seed(123)  # Set seed for reproducibility
 
 #### Simulate data ####
@@ -37,6 +38,6 @@ simulated_data <- tibble(
   )
 )
 
-# Display the first few rows of the simulated data
-head(simulated_data)
+write_parquet(simulated_data, "data/raw-data/simulated_ansur_female_data.parquet")
+write_csv(simulated_data, "data/raw-data/simulated_ansur_female_data.csv")
 

### 2024-11-28 scripts/01-test_simulate.R

@@ -1,0 +1,75 @@
+#### Preamble ####
+# Purpose: Tests the structure and validity of the simulated anthropometric and demographic dataset
+# Author: 
+# Date: 
+# Contact: 
+# License: MIT
+# Pre-requisites: 
+# - The `tidyverse` and `testthat` packages must be installed and loaded.
+# - The simulated dataset script must have been run to generate `simulated_data`.
+
+#### Workspace setup ####
+library(tidyverse)
+library(testthat)
+
+simulated_data <- read_csv("data/raw-data/simulated_ansur_female_data.csv")
+
+# Ensure `simulated_data` exists
+if (exists("simulated_data")) {
+  message("Test Passed: The simulated dataset was successfully generated.")
+} else {
+  stop("Test Failed: The simulated dataset could not be found.")
+}
+
+#### Test data ####
+
+# Test if the dataset has the correct number of rows and columns
+expected_cols <- c(
+  "weight", "height", "waist_circumference", 
+  "chest_circumference", "thigh_circumference", 
+  "biceps_circumference", "gender", "age", 
+  "ethnicity", "component"
+)
+
+# Test column names
+if (all(colnames(simulated_data) %in% expected_cols)) {
+  message("Test Passed: The dataset contains all expected columns.")
+} else {
+  stop("Test Failed: The dataset does not contain the correct columns.")
+}
+
+# Test the number of rows (expecting 1000)
+if (nrow(simulated_data) == 1000) {
+  message("Test Passed: The dataset contains the expected number of rows (1000).")
+} else {
+  stop("Test Failed: The dataset does not contain the expected number of rows.")
+}
+
+# Test for missing values
+if (all(!is.na(simulated_data))) {
+  message("Test Passed: The dataset contains no missing values.")
+} else {
+  stop("Test Failed: The dataset contains missing values.")
+}
+
+# Test for unique categories in `gender`
+if (length(unique(simulated_data$gender)) == 2) {
+  message("Test Passed: The 'gender' column contains two unique values.")
+} else {
+  stop("Test Failed: The 'gender' column does not contain the expected number of unique values.")
+}
+
+# Test for valid range of ages (should be between 18 and 60)
+if (all(simulated_data$age >= 18 & simulated_data$age <= 60)) {
+  message("Test Passed: The 'age' column contains valid values within the expected range (18-60).")
+} else {
+  stop("Test Failed: The 'age' column contains values outside the expected range.")
+}
[…]

### 2024-11-28 scripts/04-test_analysis.R

@@ -1,0 +1,50 @@
+#### Preamble ####
+# Purpose: Tests the structure and validity of the cleaned ANSUR II Female dataset
+# Author: 
+# Date: 
+# Contact:
+# License: MIT
+# Pre-requisites: 
+# - The `tidyverse` and `testthat` packages must be installed and loaded.
+# - 03-clean_data.R must have been run.
+# Any other information needed? Make sure you are in the correct R project directory.
+
+#### Workspace setup ####
+library(tidyverse)
+library(testthat)
+
+analysis_data <- read_csv("data/analysis-data/ansur_female_data.csv")
+
+
+# Test if the data was successfully loaded
+if (exists("analysis_data")) {
+  message("Test Passed: The dataset was successfully loaded.")
+} else {
+  stop("Test Failed: The dataset could not be loaded.")
+}
+
+#### Test data ####
+
+# Test if the dataset has the correct number of columns (10 expected)
+
+# Test if there are any missing values in the dataset
+if (all(!is.na(analysis_data))) {
+  message("Test Passed: The dataset contains no missing values.")
+} else {
+  stop("Test Failed: The dataset contains missing values.")
+}
+
+# Test that `component` column contains at least 2 unique values
+if (length(unique(analysis_data$component)) >= 2) {
+  message("Test Passed: The 'component' column contains at least 2 unique values.")
+} else {
+  stop("Test Failed: The 'component' column does not contain at least 2 unique values.")
+}
+
+# Check for duplicate rows
+if (nrow(analysis_data) == nrow(distinct(analysis_data))) {
+  message("Test Passed: There are no duplicate rows in the dataset.")
+} else {
+  stop("Test Failed: The dataset contains duplicate rows.")
+}
+

### 2024-11-28 scripts/05-model.R

@@ -1,0 +1,38 @@
+#### Preamble ####
+# Purpose: Create Bayesian regression model on cleaned ANSUR II Female data
+# Author:
+# Date: 
+# License: MIT
+# Pre-requisites: None
+
+#### Workspace setup ####
+library(rstanarm) # Load the rstanarm package for Bayesian modeling
+library(arrow) # Load the arrow package to read Parquet files
+library(dplyr)
+
+#### Read data ####
+cleaned_ansur_female_data <- read_parquet("data/analysis-data/ansur_female_data.parquet")
+
+#### Model data ####
+
+# Random sampling if needed
+set.seed(123)
+sampled_ansur_data <- cleaned_ansur_female_data %>%
+  sample_n(1000) 
+
+# Build a Bayesian regression model using stan_glm
+ansur_bayesian_model <- stan_glm(
+  formula = weightlbs ~ heightin + waist_circumference + thigh_circumference + age + component,
+  data = sampled_ansur_data,
+  family = gaussian(), # Specify a Gaussian family for continuous outcomes
+  prior = normal(0, 1), # Use a normal prior with mean 0 and SD 1
+  prior_intercept = normal(0, 1), # Use a normal prior for the intercept
+  seed = 123 # Set a random seed for reproducibility
+)
+
+#### Save model ####
+saveRDS(
+  ansur_bayesian_model,
+  file = "models/ansur_bayesian_model.rds"
+)
+

### 2024-11-30 paper/Exploring_the_Determinants_of_Body_Weight.qmd
Add files via upload

@@
 title: "Exploring the Determinants of Body Weight: A Bayesian Analysis of Anthropometric and Demographic Factors Among Female U.S. Army Personnel"
-subtitle: "A Bayesian Approach to Identifying Anthropometric and Demographic Predictors of Body Weight in Female U.S. Army Personnel for Improved Health Monitoring and Operational Readiness"
+subtitle: "Anthropometric Measurements Such as Waist and Thigh Circumference Are Key Predictors of Body Weight, While Demographic Factors Play a Secondary Role"
 author: 
@@
 
-Body weight is a crucial determinant of physical performance, health, and operational readiness, particularly in occupations like military service.
-In the U.S.
-Army, maintaining optimal weight is essential for meeting fitness standards, minimizing injury risks, and ensuring operational success.
-However, limited research has explored how anthropometric and demographic factors collectively influence body weight among female soldiers.
-
-This study addresses this gap using the 2012 U.S.
-Army Anthropometric Survey (ANSUR II) Female Dataset.
 The dataset contains anthropometric and demographic measurements for 1,986 female U.S.
@@
 
-By examining relationships between body weight and variables like height, waist circumference, age, and military component, this study aims to identify key predictors and develop a robust predictive model.
-The findings offer insights into the determinants of body weight and practical applications for health monitoring, fitness interventions, and military equipment design.
+While other datasets related to anthropometric measurements are publicly available, they typically focus on civilian populations or mixed-gender samples and do not offer the level of specificity needed for military personnel.
+Access to military-specific datasets is often restricted due to security and privacy concerns, making the ANSUR II dataset one of the few comprehensive sources for this population.
+This scarcity highlights the unique value of the ANSUR II dataset for understanding the anthropometric and demographic characteristics of female U.S.
+Army personnel.
 
@@
 
+## Reflecting Data Features in Model Design
+
+The model’s design reflects the characteristics of the dataset to ensure alignment with the nature of the variables and optimize the analysis.
+Anthropometric variables such as height, waist circumference, and thigh circumference were included as continuous predictors to preserve their granularity and maximize sensitivity to subtle variations in body weight.
+Age was also treated as a continuous variable, rather than being grouped into categories, to avoid arbitrary cutoffs and retain variability, enabling a more precise assessment of its relationship with body weight.
+The military component variable was modeled categorically, with each group (Regular Army, Reserves, and National Guard) treated as a distinct level to account for structural differences in activity levels and lifestyle among these groups.
+Additionally, waist and thigh circumferences were rescaled to centimeters for consistency and to reflect standard real-world measurement practices.
+These decisions ensure that the model leverages the dataset’s structure effectively while maintaining interpretability and relevance to the research context.
+
 ## Prior Distributions
@@
 
-The Bayesian regression framework was chosen for its ability to provide probabilistic estimates, which are particularly useful in quantifying uncertainty and generating credible intervals for the coefficients.
-This approach is well-suited to the study’s context, where understanding the relative influence of anthropometric and demographic predictors on body weight requires a robust and interpretable model.
-The rstanarm package was selected for its efficient handling of Bayesian inference and its built-in diagnostics, allowing for rigorous validation of the model.
-The use of a Gaussian likelihood function aligns with the continuous nature of the outcome variable (body weight), and the model’s structure avoids unnecessary complexity while accurately capturing key relationships in the data.
+A frequentist linear regression model was also considered for its simplicity and interpretability; however, it does not provide posterior distributions or credible intervals, which are essential for quantifying uncertainty in this study.
+By contrast, the Bayesian regression framework provides probabilistic estimates, enabling uncertainty quantification and credible intervals for the coefficients.
+This approach aligns well with the study’s objectives, where understanding the relative influence of predictors on body weight requires a robust and interpretable model.
+The rstanarm package was chosen for its efficient handling of Bayesian inference and built-in diagnostics, ensuring rigorous validation.
+The Gaussian likelihood function complements the continuous nature of the outcome variable (body weight), and the model structure strikes a balance between simplicity and capturing key relationships in the data.
 
@@
 By incorporating variables such as height, waist circumference, thigh circumference, age, and military component, the analysis highlights the critical role of body composition measurements in predicting body weight while accounting for demographic variability.
+These findings provide valuable insights into health monitoring and operational readiness, with implications for both military policy and broader public health initiatives.
 
@@
 
-The findings underscore the significance of anthropometric variables, particularly waist circumference and thigh circumference, as strong predictors of body weight.
-These results align with established research linking these measurements to fat distribution and muscle mass, which are key determinants of overall body weight.
-The observed positive associations reinforce the importance of these variables in health monitoring, fitness interventions, and ergonomic considerations within the military.
-While the effect of height was weaker, its inclusion as a baseline predictor remains biologically plausible and relevant for analyses of body weight variability.
+The results emphasize the significant role of anthropometric variables, particularly waist circumference and thigh circumference, as strong predictors of body weight.
+These findings align with previous research, which identify waist circumference as a key indicator of central adiposity and overall body composition [@heymsfield2015], and studies linking thigh circumference to lower body strength and fat distribution [@snijder2005].
+These measurements are critical in the military context, where body composition impacts physical performance and injury risk.
+The observed positive associations reinforce the importance of these variables in health monitoring, fitness interventions, and ergonomic considerations for military equipment design.
+
+Although height showed a weaker association with body weight, its inclusion remains biologically plausible.
+Taller individuals typically exhibit larger skeletal structures and greater overall body mass.
+This finding is consistent with literature suggesting that height, while less variable than other anthropometric measures, contributes to baseline estimations of body weight.
+These results underscore the nuanced relationships between body composition and demographic factors, offering a foundation for targeted health interventions within military populations.
 
@@
 
-Despite its contributions, this study is subject to several limitations.
-First, the dataset focuses exclusively on female personnel, limiting the generalizability of findings to other populations, including male service members or civilians.
-Second, while the dataset includes comprehensive anthropometric measurements, it lacks potentially influential variables such as physical activity levels, dietary habits, and metabolic rates.
-Incorporating these factors in future research could enhance the explanatory power and predictive accuracy of the model.
+While this study offers valuable insights, it is subject to certain limitations.
+First, the dataset focuses exclusively on female U.S.
+Army personnel, limiting the generalizability of findings to male service members or civilian populations.
+Gender differences in body composition and physical fitness have been widely documented, suggesting that extending this analysis to male personnel could uncover additional patterns.
+Future studies should aim to include a more diverse sample, encompassing multiple genders, age groups, and occupational roles.
 
-Additionally, while the Bayesian framework provides robust parameter estimates and credible intervals, future studies could benefit from hierarchical modeling to account for dependencies within subgroups, such as different military components.
-This approach would provide a more nuanced understanding of group-level differences while preserving individual-level variability.
+Second, the dataset does not account for influential lifestyle factors such as physical activity levels, dietary habits, or metabolic rates.
+These variables have been shown to significantly impact body weight and fitness outcomes.
+Including such data could improve the explanatory power and predictive accuracy of future models.
+For example, incorporating wearable fitness trackers or dietary logs might provide richer insights into the interactions between lifestyle behaviors and anthropometric measures.
 
-Expanding the scope of the dataset to include male personnel or non-military populations could enable comparative analyses and broaden the applicability of the findings.
-Future research should also explore integrating additional datasets and leveraging advanced statistical methods, such as machine learning or longitudinal analyses, to uncover dynamic relationships between body composition, fitness, and operational readiness.
+Additionally, while the Bayesian framework offers robust parameter estimates and credible intervals, hierarchical modeling could enhance the analysis by capturing subgroup-specific variations.
+For instance, dependencies within military components or geographic regions could be explored using multilevel Bayesian models, which would allow for greater precision in understanding group-level differences while preserving individual variability.
+
+Expanding the dataset’s scope to include longitudinal measurements would also enable researchers to explore dynamic relationships between body composition, fitness, and operational readiness.
+Such studies could inform policies for optimizing physical performance and reducing long-term health risks among service members.
 
@@
 
-This research underscores the utility of anthropometric measurements for predicting body weight, offering valuable insights into health monitoring, fitness interventions, and equipment design within the military.
-The findings can inform policies aimed at enhancing physical readiness and reducing injury risks among service members.
-The use of Bayesian regression models in this study further demonstrates the flexibility and interpretability of these methods for investigating complex relationships among biological and demographic factors.
+This research underscores the utility of anthropometric measurements in predicting body weight, providing actionable insights for health monitoring, fitness interventions, and military equipment design.
+For instance, the findings could guide the development of tailored fitness programs to address central adiposity (waist circumference) and muscle mass (thigh circumference), enhancing operational readiness and reducing injury risks.
+These insights align with broader public health objectives, such as the World Health Organization’s emphasis on preventing obesity-related conditions through effective weight management strategies.
 
-Looking forward, integrating more comprehensive datasets and applying advanced analytical techniques could provide deeper insights into the determinants of body weight.
-Such efforts would contribute to a better understanding of how body composition, physical fitness, and operational readiness interact over time.
-Building on the findings of this study, future research can enhance health outcomes, refine performance standards, and ultimately improve the well-being and effectiveness of military personnel.
+The use of Bayesian regression models in this study further demonstrates the flexibility and interpretability of these methods for investigating complex relationships between biological and demographic factors.
+Bayesian approaches have been increasingly recognized in health research for their ability to incorporate prior knowledge and quantify uncertainty, making them well-suited for studies involving multifactorial predictors.
+
+Looking ahead, integrating more comprehensive datasets and leveraging advanced analytical techniques, such as machine learning or longitudinal modeling, could deepen our understanding of body weight determinants.
+For example, algorithms trained on diverse datasets could identify non-linear patterns and interactions that traditional regression models might overlook.
+Such efforts would not only enhance health outcomes for military personnel but also contribute to broader efforts to improve public health, workplace ergonomics, and fitness standards across diverse populations.
 
@@
 
+To account for potential response rate challenges, oversampling could be employed within underrepresented strata, such as ethnic minorities or Reserve personnel.
+If the expected response rate is 50%, twice the number of targeted participants would be recruited within these strata to ensure adequate representation.
+Such measures would enhance the reliability of results and reduce the margin of error.
+
 To enhance the validity and reliability of the data, standardized measurement protocols would be employed during data collection.
@@
 
-# Ideal Survey Questionnaire
+# Ideal Survey Methodology
 
-## Section 1: Demographic Information
+## Survey Recruitment and Administration
+
+Respondents would be recruited using a multi-channel approach to ensure diverse participation. Recruitment channels could include:
+
+-   Direct Military Channels: Leveraging internal communication systems within the U.S. Army, such as newsletters, email campaigns, or in-person events at military bases.
+
+-   Online Platforms: Using targeted outreach through platforms like military spouse groups, service member forums, and Army-related social media networks.
+
+-   Incentives for Participation: Offering small incentives, such as participation in gift card sweepstakes or recognition within the military community, to encourage response rates.
+
+Surveys would be administered both online and in person, with the online version accessible through secure platforms like Google Forms or SurveyMonkey.
+For in-person administration, trained personnel would conduct the survey at military facilities, ensuring participants are guided through the questions.
+
+## Ideal Survey Questionnaire
+
+### Section 1: Demographic Information
 1. **What is your age?** (Open-ended)  
@@
 
-## Section 2: Anthropometric Measurements
+### Section 2: Anthropometric Measurements
 *(Instructions: Please provide accurate measurements. Measurements should be taken by a trained professional or using calibrated equipment.)*
@@
 
-## Section 3: Additional Information
+### Section 3: Additional Information
 8. **Do you have any medical conditions that may affect body weight (e.g., metabolic disorders)?** (Multiple-choice)  
@@
 
+## Validation and Quality Control
+
+To ensure high-quality responses, several validation and quality control measures would be implemented to minimize bias, enhance reliability, and ensure the accuracy of the collected data:
+
+-   Testing Protocols: The survey would be pilot-tested with a small group of personnel to identify potential ambiguities or difficulties in question interpretation.
+Pilot testing helps refine the survey design, ensuring that all questions are clear, relevant, and capable of eliciting accurate responses.
+This step minimizes measurement bias and enhances the reliability of the final data collection instrument.
+
+-   Cross-verification: Respondents would provide service branch IDs and ZIP codes for validation against military records.
+This ensures that all participants belong to the intended population (female U.S.
+Army personnel) and reduces the risk of data contamination from ineligible respondents, such as civilians or individuals outside the study's scope.
+
+-   Validation Measures: Data would be checked for completion time, with excessively short responses flagged for review.
+Duplicate entries would be identified using IP tracking for online responses.This measure helps reduce bias caused by inattentive or disengaged respondents, ensuring that the data collected reflects thoughtful and accurate input.
+
 \newpage

### 2024-11-30 paper/datasheet.qmd
Add files via upload

---
title: "Datasheet for 'Exploring the Determinants of Body Weight: A Bayesian Analysis of Anthropometric and Demographic Factors Among Female U.S. Army Personnel'"
author: 
  - Huayan Yu
thanks: "Code and data are available at: https://github.com/huayan1998/Exploring_the_Determinants_of_Body_Weight"
date: today
format: pdf
number-sections: true
bibliography: references.bib
---

Extract of the questions from @gebru2021datasheets.

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to investigate the relationship between body weight and anthropometric and demographic predictors among female U.S. Army personnel. It addresses the gap in research on female military personnel, particularly concerning their health, operational readiness, and body composition.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The dataset was created by the Natick Soldier Research, Development, and Engineering Center (NSRDEC) under the U.S. Army.
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - The dataset was funded by the U.S. Department of Defense as part of its efforts to improve operational readiness and health monitoring among military personnel.
4. *Any other comments?*
    - This dataset is one of the most comprehensive anthropometric surveys conducted on military personnel, focusing specifically on female soldiers.

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- Each instance represents an individual female U.S. Army soldier, with data points including their anthropometric measurements (e.g., height, weight, waist circumference) and demographic information (e.g., age, ethnicity, military component).
2. *How many instances are there in total (of each type, if appropriate)?*
	- The dataset contains 1,986 instances, each representing one soldier.
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- The dataset is a sample of female U.S. Army personnel from various military branches. While efforts were made to ensure representation, it is not fully representative of the entire female military population due to limitations in geographic and occupational coverage.
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- Each instance consists of raw anthropometric measurements (e.g., height, weight, waist circumference) and demographic features (e.g., age, ethnicity, and military component).
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- The target variable is body weight (in pounds), which is used to analyze its relationship with the predictors.
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- No missing information is reported, as missing values were removed during preprocessing.
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- No explicit relationships between instances exist, as each instance represents an independent individual.
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- No.
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- The dataset underwent preprocessing to remove noise and redundancies, ensuring high data quality.
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- The dataset is self-contained and does not rely on external resources.
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- No confidential information is included in the dataset.
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- No, the dataset does not contain any offensive or distressing content.
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- Sub-populations are identified by demographic variables, such as age, ethnicity, and military component. These distributions are reported in the dataset documentation.
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- No, individuals cannot be identified directly or indirectly.
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- The dataset includes sensitive demographic data such as ethnicity and age, but these are anonymized and used solely for analysis.
16. *Any other comments?*
	- No.

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- Anthropometric data (e.g., height, weight, waist circumference) was directly observed and measured using calibrated tools by trained personnel. Demographic data (e.g., age, ethnicity, military component) was self-reported and cross-verified against administrative records for accuracy.
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- Data was collected using calibrated instruments such as stadiometers, measuring tapes, and calipers for anthropometric measurements. Manual entry was used for demographic data, with verification against official military records to ensure reliability.
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- The dataset was derived using a stratified random sampling strategy to ensure representation across military components (Active Duty, Reserves, National Guard), age groups, and ethnicities.
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- Data collection was conducted by trained personnel under the supervision of the Natick Soldier Research, Development, and Engineering Center (NSRDEC). Compensation details were not explicitly mentioned but likely followed standard military protocols.
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- Data was collected between 2010 and 2012, aligning with the time when the measurements were taken.
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- Ethical considerations were likely reviewed as part of the U.S. Army's internal processes for human data collection, though explicit documentation is not provided.
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- Website.
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- Participants were likely informed as part of the data collection process conducted under military protocols, though specific notification details are not provided.
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- Consent was likely obtained in accordance with standard military data collection procedures, though specific consent forms or language are not available.
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- No explicit mechanism for revoking consent is mentioned, as the data collection was part of military operations.
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- No specific data protection impact analysis is mentioned, but the data is anonymized to protect individual identities.
12. *Any other comments?*
	- No.

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- Yes, preprocessing was performed, including removing missing values, renaming variables for consistency, and scaling measurements (e.g., converting waist circumference from millimeters to centimeters).
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- The raw data was retained in its original form for future reference and potential reanalysis.
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- The preprocessing was performed using R, and the scripts are available in the project repository.
4. *Any other comments?*
	- No.

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- Cannot find any. 
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- Cannot find any. 
3. *What (other) tasks could the dataset be used for?*
	- The dataset could be used for health monitoring, ergonomic research, fitness program optimization, and studies on gender-specific anthropometric trends.
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- Consumers should be cautious about generalizing findings beyond female U.S. Army personnel, as the dataset is not representative of broader populations.
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- The dataset should not be used for identifying individuals or making decisions that could unfairly impact subgroups without additional validation.
6. *Any other comments?*
	- No.

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- Yes, the dataset is publicly available and can be accessed by researchers or institutions interested in anthropometric studies or military health monitoring.
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The dataset is distributed via Data World (https://data.world/datamil/ansur-ii-female). It does not have a DOI.
3. *When will the dataset be distributed?*
	- The dataset has already been distributed and is publicly accessible.
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- The dataset is distributed under a public license with terms outlined on the Data World platform. There are no fees associated with its use for research purposes.
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- Cannot find any.
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- No export controls or regulatory restrictions apply to the dataset.
7. *Any other comments?*
	- The dataset is easily accessible and designed for educational and research purposes.

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- The dataset is hosted and maintained by Data World and the original creators at the Natick Soldier Research, Development, and Engineering Center.
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- The dataset curators can be contacted through the Data World platform.
3. *Is there an erratum? If so, please provide a link or other access point.*
	- No formal erratum has been issued.
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- The dataset is static and unlikely to receive updates. Any changes would be communicated through the Data World platform.
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- There are no explicit retention limits, as the dataset is anonymized and publicly available.
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- The dataset is not expected to undergo major changes, so the current version will remain accessible indefinitely.
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- There is no formal mechanism for external contributions to this dataset.
8. *Any other comments?*
	- The dataset is intended as a standalone resource for academic and research purposes, with no current plans for collaborative updates.

\newpage

# References

### 2024-12-02 scripts/02-clean_data.R
Delete scripts/02-clean_data.R

@@ -1,39 +1,0 @@
-#### Preamble ####
-# Purpose: Cleans the raw ANSUR II Female Dataset for analysis
-# Author: 
-# Date: 
-# License: MIT
-# Pre-requisites: Raw ANSUR II Female data must be available in the specified directory.
-
-#### Workspace setup ####
-library(tidyverse)
-library(janitor) # For clean_names()
-library(tidyr)   # For drop_na()
-
-#### Clean data ####
-# Load the raw data
-raw_data <- read_csv("data/raw-data/ansur_female_data.csv")
-
-# Clean and prepare the data
-cleaned_data <- 
-  raw_data |>
-  janitor::clean_names() |>  # Standardize column names
-  select( weightlbs, heightin, waistcircumference, 
-         thighcircumference, age, component) |>  # Select relevant variables
-  drop_na() |>  # Remove rows with missing values
-  mutate(
-    # Convert character columns to appropriate types if necessary
-    component = as.factor(component),
-    age = as.numeric(age),
-    waistcircumference = waistcircumference / 10,
-    thighcircumference = thighcircumference / 10
-  ) |> 
-  rename(
-    waist_circumference = waistcircumference,
-    thigh_circumference = thighcircumference,
-  )
-
-#### Save data ####
-write_csv(cleaned_data, "data/analysis-data/ansur_female_data.csv")
-write_parquet(cleaned_data, "data/analysis-data/ansur_female_data.parquet")
-

### 2024-12-02 scripts/03-test_analysis.R
Delete scripts/03-test_analysis.R

@@ -1,50 +1,0 @@
-#### Preamble ####
-# Purpose: Tests the structure and validity of the cleaned ANSUR II Female dataset
-# Author: [Your Name] [...UPDATE THIS...]
-# Date: [Today's Date] [...UPDATE THIS...]
-# Contact: [Your Contact Information] [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: 
-# - The `tidyverse` and `testthat` packages must be installed and loaded.
-# - 03-clean_data.R must have been run.
-# Any other information needed? Make sure you are in the correct R project directory.
-
-#### Workspace setup ####
-library(tidyverse)
-library(testthat)
-
-analysis_data <- read_csv("data/analysis-data/ansur_female_data.csv")
-
-
-# Test if the data was successfully loaded
-if (exists("analysis_data")) {
-  message("Test Passed: The dataset was successfully loaded.")
-} else {
-  stop("Test Failed: The dataset could not be loaded.")
-}
-
-#### Test data ####
-
-# Test if the dataset has the correct number of columns (10 expected)
-
-# Test if there are any missing values in the dataset
-if (all(!is.na(analysis_data))) {
-  message("Test Passed: The dataset contains no missing values.")
-} else {
-  stop("Test Failed: The dataset contains missing values.")
-}
-
-# Test that `component` column contains at least 2 unique values
-if (length(unique(analysis_data$component)) >= 2) {
-  message("Test Passed: The 'component' column contains at least 2 unique values.")
-} else {
-  stop("Test Failed: The 'component' column does not contain at least 2 unique values.")
-}
-
-# Check for duplicate rows
-if (nrow(analysis_data) == nrow(distinct(analysis_data))) {
-  message("Test Passed: There are no duplicate rows in the dataset.")
-} else {
-  stop("Test Failed: The dataset contains duplicate rows.")
-}
-

### 2024-12-02 scripts/04-model.R
Delete scripts/04-model.R

@@ -1,38 +1,0 @@
-#### Preamble ####
-# Purpose: Create Bayesian regression model on cleaned ANSUR II Female data
-# Author:
-# Date: 
-# License: MIT
-# Pre-requisites: None
-
-#### Workspace setup ####
-library(rstanarm) # Load the rstanarm package for Bayesian modeling
-library(arrow) # Load the arrow package to read Parquet files
-library(dplyr)
-
-#### Read data ####
-cleaned_ansur_female_data <- read_parquet("data/analysis-data/ansur_female_data.parquet")
-
-#### Model data ####
-
-# Random sampling if needed
-set.seed(123)
-sampled_ansur_data <- cleaned_ansur_female_data %>%
-  sample_n(1000) 
-
-# Build a Bayesian regression model using stan_glm
-ansur_bayesian_model <- stan_glm(
-  formula = weightlbs ~ heightin + waist_circumference + thigh_circumference + age + component,
-  data = sampled_ansur_data,
-  family = gaussian(), # Specify a Gaussian family for continuous outcomes
-  prior = normal(0, 1), # Use a normal prior with mean 0 and SD 1
-  prior_intercept = normal(0, 1), # Use a normal prior for the intercept
-  seed = 123 # Set a random seed for reproducibility
-)
-
-#### Save model ####
-saveRDS(
-  ansur_bayesian_model,
-  file = "models/ansur_bayesian_model.rds"
-)
-

### 2024-12-02 paper/paper.qmd
update paper, scripts, references

--- 2024-11-30 paper/Exploring_the_Determinants_of_Body_Weight.qmd
@@
 
-# Introduction {#sec-intro}
+# Introduction
 
-Body weight significantly influences physical performance, health, and operational readiness in demanding occupations like military service.
-In the U.S.
-Army, maintaining optimal weight is essential for meeting fitness standards, minimizing injury risks, and ensuring operational efficiency.
-Despite the availability of extensive anthropometric and demographic data, limited research examines how these factors collectively impact body weight, particularly among female soldiers [@gordon2014].
+Body weight plays a critical role in physical performance, health, and operational readiness, particularly in demanding professions such as military service.
+For the U.S.
+Army, maintaining optimal weight is crucial to meet fitness standards, reduce injury risks, and ensure operational efficiency.
+While extensive anthropometric and demographic data exist, limited research explores the combined influence of these factors on body weight, particularly among female soldiers [@gordon2014].
 
-This study addresses this gap using the 2012 U.S.
-Army Anthropometric Survey (ANSUR II) Female Dataset, which includes rigorous anthropometric and demographic measurements of female personnel.
-Data collection employed standardized instruments, such as stadiometers and calipers, ensuring consistency and reliability [@hotzman2011; @paquette2009].
-Variables like height, waist circumference, and thigh circumference were measured to capture body composition, while demographic data such as age, ethnicity, and military component were cross-verified with administrative records [@gordon2014].
+This study addresses this gap by leveraging the 2012 U.S.
+Army Anthropometric Survey (ANSUR II) Female Dataset, which includes precise anthropometric and demographic measurements of female personnel.
+Data collection utilized standardized instruments such as stadiometers and calipers, ensuring high reliability and consistency [@hotzman2011; @paquette2009].
+Key variables, including height, waist circumference, and thigh circumference, were measured to assess body composition, while demographic factors such as age, ethnicity, and military component were cross-validated with administrative records [@gordon2014].
 
-The analysis highlights anthropometric variables as strong predictors of body weight and demographic factors as additional contributors.
-These findings support personalized fitness programs, improved health outcomes, and optimized military gear for enhancing operational readiness [@opendesignlab2018; @paquette2009].
+The primary aim of this study is to model the relationship between body weight and a set of anthropometric and demographic predictors among female U.S.
+Army personnel.
+Specifically, it quantifies how variations in measurements such as height and waist circumference, alongside demographic factors like age and ethnicity, contribute to body weight.
+The goal is to identify significant predictors and develop a robust predictive model that can inform health monitoring, tailored fitness programs, and ergonomic equipment design.
 
-This paper is organized as follows: Section [@sec-intro] provides an overview of the study's background and objectives.
-Section [@sec-data] introduces the dataset and offers an analysis of key variables.
-Section [@sec-model] details the methodology, including the Bayesian regression model employed.
-Section [@sec-result] presents the results, emphasizing the significance of predictors and model performance.
-Section [@sec-discussion] explores the study's limitations and provides directions for future research.
-Lastly, Section [@sec-model-details] presents posterior predictive checks, diagnostic plots, and their interpretations.
+Preliminary findings underscore the strong predictive power of anthropometric variables in determining body weight, with demographic factors serving as additional contributors.
+These insights support the development of personalized fitness interventions, improved health outcomes, and the optimization of military gear to enhance operational readiness [@opendesignlab2018; @paquette2009].
 
-## Estimand
-
-This study seeks to estimate the relationship between body weight and a set of key anthropometric and demographic variables among female U.S.
-Army personnel.
-Specifically, it aims to quantify how variations in anthropometric measurements, such as height and waist circumference, as well as demographic factors, including age and ethnicity, influence body weight.
-The objective is to identify significant predictors and develop a robust predictive model to enhance understanding and practical applications in health monitoring, fitness interventions, and equipment design.
+This paper is structured as follows: [@sec-data] describes the dataset and provides a descriptive analysis of the key variables.
+[@sec-model] explains the methodology, including the Bayesian regression model employed.
+[@sec-result] presents the findings, highlighting significant predictors and model performance.
+[@sec-discussion] discusses the implications, limitations, and future research directions.
+Lastly, [@sec-model-details] offers detailed posterior predictive checks, diagnostic plots, and their interpretations.
 
 # Data {#sec-data}
+
+The ANSUR II dataset provides comprehensive anthropometric and demographic data for 1,986 female U.S [@ansurII_female].
+Army personnel, collected using standardized protocols to ensure accuracy.
+Unlike civilian datasets, it uniquely addresses the physical demands and characteristics of military personnel, offering rare insights into factors like fitness, injury risk, and gear design [@hotzman2011].
+Its specificity makes it a vital resource for understanding and improving the health, safety, and operational readiness of female soldiers [@paquette2009].
 
@@
 #| message: false
-
 library(tidyverse)
 library(tinytable)
-library(dplyr)
 library(arrow)
 library(knitr)
-library(ggplot2)
 
 # Load the dataset
-file_path <- "../data/analysis-data/ansur_female_data.csv" 
-ansur_female <- read_csv(file_path)
-
+analysis_data <- read_parquet(here::here("data", "02-analysis_data", "analysis_data.parquet"))
 ```
@@
 
-The dataset contains anthropometric and demographic measurements for 1,986 female U.S.
-Army personnel, collected by the Natick Soldier Research, Development, and Engineering Center (NSRDEC) using standardized protocols.
-Variables such as stature, waist circumference, and chest circumference were measured with precise instruments, while demographic data like age and military component were cross-verified with administrative records to ensure accuracy.
+The dataset comprises anthropometric and demographic measurements from 1,986 female U.S.
+Army personnel, meticulously collected by the Natick Soldier Research, Development, and Engineering Center (NSRDEC) as part of the 2012 ANSUR II survey.
+Anthropometric variables such as stature, waist circumference, chest circumference, and thigh circumference were measured using standardized protocols with high-precision instruments, including stadiometers, calipers, and tape measures.
+To ensure accuracy and reliability, the data collection process adhered to rigorous methodological standards, minimizing variability and measurement error.
+Demographic variables, including age, ethnicity, and military component (e.g., Regular Army, Reserve), were cross-referenced with administrative records, further enhancing the validity of the dataset.
 
-While other datasets related to anthropometric measurements are publicly available, they typically focus on civilian populations or mixed-gender samples and do not offer the level of specificity needed for military personnel.
-Access to military-specific datasets is often restricted due to security and privacy concerns, making the ANSUR II dataset one of the few comprehensive sources for this population.
-This scarcity highlights the unique value of the ANSUR II dataset for understanding the anthropometric and demographic characteristics of female U.S.
+Although other publicly available datasets focus on anthropometric measurements, they are typically centered on civilian populations or mixed-gender samples, which do not capture the unique physical demands and requirements of military personnel.
+Civilian datasets often lack the granularity necessary to account for the operational and performance-based contexts of military service, where precise body measurements can impact everything from uniform design to load-bearing capacity and overall readiness.
+Moreover, military-specific datasets are rarely accessible to researchers due to stringent security and privacy concerns, creating a significant gap in publicly available data for this specialized group.
+
+The ANSUR II dataset bridges this gap by providing one of the most comprehensive sources of anthropometric and demographic data specific to female military personnel.
+This specificity is crucial for understanding the physical characteristics and needs of female soldiers, who face unique challenges compared to their male counterparts.
+The dataset's depth allows researchers to analyze relationships between body dimensions and factors such as physical performance, injury risk, and operational readiness.
+Furthermore, it offers valuable insights for developing tailored fitness programs, improving gear design, and enhancing overall health and safety standards in military contexts.
+
+Given its rarity and specificity, the ANSUR II dataset is an invaluable resource for researchers and policymakers interested in advancing the well-being and effectiveness of female U.S.
 Army personnel.
+By enabling analyses that would otherwise be impossible with civilian datasets, it contributes to a deeper understanding of the unique anthropometric and demographic characteristics of this population, paving the way for evidence-based interventions and policy decisions.
 
@@
 
-The data for this study was systematically downloaded, cleaned, analyzed, modeled, and visualized using R [@citeR], an extensive statistical programming language.
-The following packages were used for this study:
+The `tidyverse` package [@tidyverse] was used to streamline the entire process of data manipulation, transformation, and visualization, ensuring consistency, efficiency, and flexibility throughout the analysis.
+Its comprehensive suite of tools enabled the creation of tailored and informative visual outputs, as well as the effective transformation and summarization of complex datasets.
 
-- **`tidyverse`** [@tidyverse]: To streamline the process of data manipulation and visualization.
-- **`ggplot2`** [@ggplot2]: Used for its powerful and flexible capabilities in creating various types of visualizations tailored to the needs of this study.
-- **`dplyr`** [@dplyr]: Employed for its intuitive functions to transform and summarize complex datasets effectively.
-- **`rstanarm`** [@rstanarm]: Facilitated the implementation of Bayesian models, providing a straightforward way to fit regression models using Stan.
-- **`bayesplot`** [@bayesplot]: Utilized for creating graphical posterior predictive checks and diagnostic plots to assess model fit.
-- **`arrow`** [@arrow]: Used for efficiently reading and writing large datasets, enhancing data handling capabilities.
-- **`tinytable`** [@tinytable]: Used to create compact and well-organized summary tables for presenting data and model outputs effectively.
-- **`modelsummary`** [@modelsummary]: Used for creating professional-quality regression tables and visualizations to summarize model results clearly.
-- **`knitr`** [@knitr]: Employed to dynamically generate reproducible reports that integrate R code with its outputs, allowing for seamless inclusion of plots and analysis results in the final document.
-- **`janitor`** [@janitor]: Used for its efficient data cleaning functions, simplifying the process of preprocessing dirty data into a clean, analysis-ready format.
-- **_Telling Stories with Data_** [@tellingstories]: This book was consulted for its statistical information.
+The implementation of Bayesian models was facilitated by `rstanarm` [@rstanarm], which provided a straightforward way to fit regression models using Stan.
+Diagnostic and posterior predictive checks were conducted using `bayesplot` [@bayesplot], allowing for thorough assessment of model fit through graphical outputs.
+The `arrow` package [@arrow] enhanced data handling by enabling efficient reading and writing of large datasets.
 
-```{r}
-#| label: tbl-head-data
-#| tbl-cap: First 6 rows of the cleaned dataset
-#| echo: false
-#| warning: false
-#| message: false
+To present data and model outputs effectively, `tinytable` [@tinytable] was used to create compact and well-organized summary tables, while `modelsummary` [@modelsummary] provided professional-quality regression tables and visualizations, ensuring clarity in summarizing model results.
+Dynamic and reproducible reporting was achieved with `knitr` [@knitr], integrating R code with outputs for seamless inclusion of plots and analysis in the final document.
+For data cleaning, `janitor` [@janitor] was instrumental in preprocessing dirty data into a clean, analysis-ready format.
 
-ansur_female |>
-  head() |>
-  kable(booktabs = TRUE, align = "c")
-```
+Finally, the book Telling Stories with Data [@tellingstories] was consulted as a statistical reference, providing valuable insights to support the analysis and visualization strategies employed in this study.
 
@@
 
-### Body Weight in Pounds {#sec-body-weight}
+### Body Weight in Pounds
 
@@
 
-ggplot(data = ansur_female, aes(x = weightlbs)) +
+ggplot(data = analysis_data, aes(x = weightlbs)) +
   geom_histogram(binwidth = 2, fill = "steelblue", color = "grey50") +
@@
   theme(plot.title = element_text(hjust = 0.5))
-
 ```
@@
 
-### Height {#sec-height}
+### Height
 
@@
 
-ggplot(data = ansur_female, aes(x = heightin)) +
+ggplot(data = analysis_data, aes(x = heightin)) +
   geom_histogram(binwidth = 2, fill = "darkgreen", color = "grey50") +
@@
   theme(plot.title = element_text(hjust = 0.5))
-
 ```
 
-### Waist Circumference {#sec-waist-circumference}
+### Waist Circumference
 
@@
 
-### Thigh Circumference {#sec-thigh-circumference}
+### Thigh Circumference
 
@@
 # Example dataset (use your cleaned data instead)
-data <- ansur_female
+data <- analysis_data
 
@@
   theme(legend.position = "none")
-
 ```
 
-### Age {#sec-age}
+### Age
 
@@
 # Summary statistics for age
-age_summary <- ansur_female %>%
+age_summary <- analysis_data %>%
   summarise(
@@
 age_table
-
 ```
 
-### Component {#sec-component}
+### Component
 
@@
 # Frequency table for component
-component_summary <- ansur_female %>%
+component_summary <- analysis_data %>%
   count(component) %>%
@@
 component_table
-
 ```
@@
 
-The model’s design reflects the characteristics of the dataset to ensure alignment with the nature of the variables and optimize the analysis.
+The model's design reflects the characteristics of the dataset to ensure alignment with the nature of the variables and optimize the analysis.
 Anthropometric variables such as height, waist circumference, and thigh circumference were included as continuous predictors to preserve their granularity and maximize sensitivity to subtle variations in body weight.
@@
 Additionally, waist and thigh circumferences were rescaled to centimeters for consistency and to reflect standard real-world measurement practices.
-These decisions ensure that the model leverages the dataset’s structure effectively while maintaining interpretability and relevance to the research context.
+These decisions ensure that the model leverages the dataset's structure effectively while maintaining interpretability and relevance to the research context.
 
@@
 
--   Intercept Priors: For the model’s intercept $\beta_0$, a normal prior distribution is used with a mean of 0 and a standard deviation of 1.
+-   Intercept Priors: For the model's intercept $\beta_0$, a normal prior distribution is used with a mean of 0 and a standard deviation of 1.
 This choice reflects the assumption that the baseline body weight (when all predictors are zero) is centered near the observed scale of the outcome variable but avoids imposing overly strong constraints.
@@
 
-The weakly informative priors are designed to enhance the model’s robustness, ensuring credible parameter estimates and reliable uncertainty quantification.
+The weakly informative priors are designed to enhance the model's robustness, ensuring credible parameter estimates and reliable uncertainty quantification.
 The use of Bayesian priors provides an added layer of rigor, particularly when estimating complex relationships between predictors and body weight.
@@
 By contrast, the Bayesian regression framework provides probabilistic estimates, enabling uncertainty quantification and credible intervals for the coefficients.
-This approach aligns well with the study’s objectives, where understanding the relative influence of predictors on body weight requires a robust and interpretable model.
+This approach aligns well with the study's objectives, where understanding the relative influence of predictors on body weight requires a robust and interpretable model.
 The rstanarm package was chosen for its efficient handling of Bayesian inference and built-in diagnostics, ensuring rigorous validation.
@@
 The predictors included height, waist circumference, thigh circumference, age, and military component.
-The analysis identified significant positive associations between body weight and the anthropometric predictors—height, waist circumference, and thigh circumference—highlighting their strong influence on body weight.
+The analysis identified significant positive associations between body weight and the anthropometric predictors---height, waist circumference, and thigh circumference---highlighting their strong influence on body weight.
 Age and military component demonstrated smaller but meaningful effects, reflecting their nuanced contributions to variations in body weight.
@@
 library(rstanarm)
-ansur_bayesian_model <-
-  readRDS(file = here::here("models/ansur_bayesian_model.rds"))
-
+bayesian_model <-
+  readRDS(file = here::here("models/bayesian_model.rds"))
 ```
@@
 modelsummary(
-  list("Bayesian Regression Model" = ansur_bayesian_model),
+  list("Bayesian Regression Model" = bayesian_model),
   statistic = c("conf.int", "std.error"), # Include credible intervals and standard errors
@@
 )
-
 ```
@@
 
-The model’s intercept represents the baseline body weight when all predictors are at their reference levels or zero.
+The model's intercept represents the baseline body weight when all predictors are at their reference levels or zero.
 While this value lacks direct interpretability due to the unrealistic scenario of zero predictors, it provides a conceptual starting point for the model.
@@
 
-posterior <- as.matrix(ansur_bayesian_model)
+posterior <- as.matrix(bayesian_model)
 
@@
   posterior,
-  pars = c("(Intercept)", "heightin", "waist_circumference", "thigh_circumference", "age", "componentArmy Reserve", "componentRegular Army"),
+  pars = c("heightin", "waist_circumference", "thigh_circumference", "age", "componentArmy Reserve", "componentRegular Army"),
   prob = 0.89, # 89% credible intervals
@@
   theme_classic()
-
 ```
@@
 These results affirm the utility of anthropometric data in health monitoring and fitness interventions while identifying areas for further refinement.
-Exploring additional predictors may enhance the model’s explanatory power and improve its utility in practical applications.
+Exploring additional predictors may enhance the model's explanatory power and improve its utility in practical applications.
 
@@
 
+## Broader Implications for Health and Military Readiness
+
+This research underscores the utility of anthropometric measurements in predicting body weight, providing actionable insights for health monitoring, fitness interventions, and military equipment design.
+For instance, the findings could guide the development of tailored fitness programs to address central adiposity (waist circumference) and muscle mass (thigh circumference), enhancing operational readiness and reducing injury risks.
+These insights align with broader public health objectives, such as the World Health Organization's emphasis on preventing obesity-related conditions through effective weight management strategies.
+
+The use of Bayesian regression models in this study further demonstrates the flexibility and interpretability of these methods for investigating complex relationships between biological and demographic factors.
+Bayesian approaches have been increasingly recognized in health research for their ability to incorporate prior knowledge and quantify uncertainty, making them well-suited for studies involving multifactorial predictors.
+
+Looking ahead, integrating more comprehensive datasets and leveraging advanced analytical techniques, such as machine learning or longitudinal modeling, could deepen our understanding of body weight determinants.
+For example, algorithms trained on diverse datasets could identify non-linear patterns and interactions that traditional regression models might overlook.
+Such efforts would not only enhance health outcomes for military personnel but also contribute to broader efforts to improve public health, workplace ergonomics, and fitness standards across diverse populations.
+
 ## Limitations and Future Directions
@@
 
-Expanding the dataset’s scope to include longitudinal measurements would also enable researchers to explore dynamic relationships between body composition, fitness, and operational readiness.
+Expanding the dataset's scope to include longitudinal measurements would also enable researchers to explore dynamic relationships between body composition, fitness, and operational readiness.
 Such studies could inform policies for optimizing physical performance and reducing long-term health risks among service members.
-
-## Broader Implications for Health and Military Readiness
-
-This research underscores the utility of anthropometric measurements in predicting body weight, providing actionable insights for health monitoring, fitness interventions, and military equipment design.
-For instance, the findings could guide the development of tailored fitness programs to address central adiposity (waist circumference) and muscle mass (thigh circumference), enhancing operational readiness and reducing injury risks.
-These insights align with broader public health objectives, such as the World Health Organization’s emphasis on preventing obesity-related conditions through effective weight management strategies.
-
-The use of Bayesian regression models in this study further demonstrates the flexibility and interpretability of these methods for investigating complex relationships between biological and demographic factors.
-Bayesian approaches have been increasingly recognized in health research for their ability to incorporate prior knowledge and quantify uncertainty, making them well-suited for studies involving multifactorial predictors.
-
-Looking ahead, integrating more comprehensive datasets and leveraging advanced analytical techniques, such as machine learning or longitudinal modeling, could deepen our understanding of body weight determinants.
-For example, algorithms trained on diverse datasets could identify non-linear patterns and interactions that traditional regression models might overlook.
-Such efforts would not only enhance health outcomes for military personnel but also contribute to broader efforts to improve public health, workplace ergonomics, and fitness standards across diverse populations.
 
@@
 First, the raw dataset was loaded using the read_csv function and processed with the janitor::clean_names() function to standardize column names, making them easier to interpret and work with.
-Key variables relevant to the study—such as weight (weightlbs), height (heightin), waist circumference, thigh circumference, age, and military component—were selected using the select() function to focus the analysis on predictors of interest.
+Key variables relevant to the study---such as weight (weightlbs), height (heightin), waist circumference, thigh circumference, age, and military component---were selected using the select() function to focus the analysis on predictors of interest.
 
@@
 [@fig-ppcheckandposteriorvsprior-1] presents a posterior predictive check to evaluate how well the model predicts the observed data.
-This diagnostic compares the simulated data from the model’s posterior distribution with the actual observed data, providing insights into the model's adequacy.
+This diagnostic compares the simulated data from the model's posterior distribution with the actual observed data, providing insights into the model's adequacy.
 A good fit is characterized by overlapping distributions of predicted and observed values, indicating that the model effectively captures key characteristics of the data.
@@
 #| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
-
-library(here)
-
-file_path <- here::here("data", "analysis-data", "ansur_female_data.parquet")
-
-# Check if the file exists before attempting to read
-if (file.exists(file_path)) {
-  sampled_ansur_data <- read_parquet(file_path) %>%
-    sample_n(1000)  # Sample 1000 rows
-} else {
-  stop("File not found: ", file_path)
-}
-pp_check(ansur_bayesian_model) +
+pp_check(bayesian_model) +
   theme_classic() +
@@
 
-posterior_vs_prior(ansur_bayesian_model) +
+posterior_vs_prior(bayesian_model) +
   theme_minimal() +
@@
   coord_flip()
-
 ```
@@
 The consistent overlap of chains indicates that the sampling algorithm has effectively explored the posterior distribution.
-These results suggest that the Bayesian model’s estimates are reliable and not overly sensitive to initial values or random sampling variation.
+These results suggest that the Bayesian model's estimates are reliable and not overly sensitive to initial values or random sampling variation.
 
@@
 
-plot(ansur_bayesian_model, "trace")
-
-plot(ansur_bayesian_model, "rhat")
-
+plot(bayesian_model, "trace")
+plot(bayesian_model, "rhat")
 ```
-
-# Ideal Data Sampling Methodology
-
-In an ideal scenario, the data for this study would be collected using a stratified random sampling method to ensure the sample accurately represents the diverse population of female U.S.
-Army personnel.
-This approach would involve dividing the population into distinct strata based on key demographic and occupational characteristics, such as military component (Active Duty, Reserves, National Guard), age groups (e.g., 18–25, 26–35, 36+ years), and ethnic backgrounds.
-Each stratum would then be sampled independently, with participants randomly selected within each group in proportion to their representation in the overall population.
-Stratified random sampling is particularly effective for heterogeneous populations, as it minimizes sampling bias and ensures that smaller subgroups, such as Reserve personnel or older age groups, are adequately represented.
-
-To implement this method, a comprehensive roster of all female U.S.
-Army personnel would be required.
-This roster would include essential demographic and occupational information to accurately classify individuals into strata.
-Once stratification is complete, participants would be selected using randomization techniques, such as computer-generated random numbers, to eliminate selection bias.
-For instance, if 50% of the total population comprises Active Duty personnel, 50% of the sampled participants would also be drawn from this stratum.
-Similarly, if 20% of personnel fall within the 18–25 age group, this age group would constitute 20% of the sample.
-This proportional allocation ensures that the sample mirrors the characteristics of the entire population.
-
-To account for potential response rate challenges, oversampling could be employed within underrepresented strata, such as ethnic minorities or Reserve personnel.
-If the expected response rate is 50%, twice the number of targeted participants would be recruited within these strata to ensure adequate representation.
-Such measures would enhance the reliability of results and reduce the margin of error.
-
-To enhance the validity and reliability of the data, standardized measurement protocols would be employed during data collection.
-Anthropometric measurements, such as weight, height, waist circumference, and thigh circumference, would be conducted using calibrated instruments and performed by trained professionals to reduce variability.
-Demographic data, such as age, ethnicity, and military component, would be collected through self-reports and cross-verified with official administrative records to ensure accuracy and consistency.
 
@@
 
-## Survey Recruitment and Administration
+## Budget Allocation
 
-Respondents would be recruited using a multi-channel approach to ensure diverse participation. Recruitment channels could include:
+To implement the survey effectively, a budget of \$60,000 has been allocated across key components.
+Recruitment efforts are estimated to cost \$10,000, including expenses for email campaigns, newsletters, physical flyers, and outreach via social media platforms.
+Incentives, such as gift cards or community recognition, are also included to encourage participation.
+Data collection accounts for \$25,000, covering the training of professionals, purchasing and calibrating measurement equipment, licensing survey platforms, and logistics for in-person survey administration.
+Statistical sampling and quality control measures, such as stratified random sampling, cross-verification, and pilot testing, are allocated \$15,000.
+Finally, \$10,000 is designated for data analysis and report preparation, ensuring comprehensive reporting and stakeholder communication.
 
--   Direct Military Channels: Leveraging internal communication systems within the U.S. Army, such as newsletters, email campaigns, or in-person events at military bases.
+## Recruitment Strategy
 
--   Online Platforms: Using targeted outreach through platforms like military spouse groups, service member forums, and Army-related social media networks.
+A multi-channel approach will be employed to recruit participants and ensure representation across all military components.
+Direct outreach through internal military communication systems, including email campaigns, newsletters, and base announcements, will be complemented by online recruitment via social media groups and forums frequented by U.S.
+Army personnel.
+In-person recruitment efforts, such as hosting information sessions and setting up booths at military installations, will further support participant engagement.
+To maximize response rates, incentives like gift cards or recognition within the military community will be offered.
 
--   Incentives for Participation: Offering small incentives, such as participation in gift card sweepstakes or recognition within the military community, to encourage response rates.
+## Sampling Method
 
-Surveys would be administered both online and in person, with the online version accessible through secure platforms like Google Forms or SurveyMonkey.
-For in-person administration, trained personnel would conduct the survey at military facilities, ensuring participants are guided through the questions.
+The study will utilize a stratified random sampling approach to ensure the sample accurately reflects the diverse population of female U.S.
+Army personnel.
+Strata will be defined based on military component (Active Duty, Reserves, National Guard), age groups (18–25, 26–35, 36+ years), and ethnic backgrounds.
+Participants will be randomly selected within each stratum using computer-generated random numbers, with proportional allocation to mirror population distribution.
+To ensure adequate representation of smaller groups, such as Reserve personnel or minority ethnic groups, oversampling will be applied, doubling the sample size in these strata to address potential non-response challenges.
+
+## Data Collection Process
+
+Anthropometric measurements, including weight, height, waist circumference, and thigh circumference, will be conducted by trained professionals using calibrated instruments to ensure precision and reliability.
+Demographic data, such as age, ethnicity, and military component, will be collected via self-reported survey responses and cross-verified with administrative records.
+Surveys will be administered online using secure platforms like Qualtrics or SurveyMonkey, while in-person administration at military facilities will provide accessibility for personnel without internet access.
+This dual-mode approach ensures flexibility and inclusivity in data collection.
+
+## Quality Control and Validation
+
+To ensure data accuracy and reliability, several quality control measures will be implemented.
+Responses will be cross-verified with military records to validate demographic information.
+Pilot testing will be conducted with a small, diverse sample to refine survey questions and address logistical challenges.
+Response quality will be assessed by reviewing response times and identifying duplicates using IP tracking for online submissions.
+Measurement validation protocols, including regular calibration of equipment and standardization of procedures, will minimize variability.
+Ethical compliance will be ensured through Institutional Review Board (IRB) approval, and data privacy will be safeguarded through anonymization and encryption.
+
+This comprehensive methodology ensures robust, accurate, and representative data collection while addressing practical, ethical, and logistical considerations.
+By employing stratified random sampling, rigorous data validation, and inclusive recruitment strategies, the study is well-positioned to deliver valuable insights into the determinants of body weight among female U.S.
+Army personnel.
 
@@
 ### Section 1: Demographic Information
-1. **What is your age?** (Open-ended)  
+
+1.  **What is your age?** (Open-ended)\
     Example answer: 25
@@
 2.  **Which military component are you currently serving in?** (Multiple-choice)
-   - Regular Army  
-   - Army Reserve  
+
+    -   Regular Army\
+    -   Army Reserve\
     -   National Guard
@@
 3.  **What is your ethnic background?** (Multiple-choice)
-   - White  
-   - Black or African American  
-   - Asian  
-   - Hispanic or Latino  
-   - Native American or Alaska Native  
-   - Native Hawaiian or Pacific Islander  
-   - Other (please specify): ___________
+
+    -   White\
+    -   Black or African American\
+    -   Asian\
+    -   Hispanic or Latino\
+    -   Native American or Alaska Native\
+    -   Native Hawaiian or Pacific Islander\
+    -   Other (please specify): \_\_\_\_\_\_\_\_\_\_\_
 
 ### Section 2: Anthropometric Measurements
+
 *(Instructions: Please provide accurate measurements. Measurements should be taken by a trained professional or using calibrated equipment.)*
 
-4. **What is your body weight in pounds?** (Open-ended)  
+4.  **What is your body weight in pounds?** (Open-ended)\
     Example answer: 142
 
-5. **What is your height in inches?** (Open-ended)  
+5.  **What is your height in inches?** (Open-ended)\
     Example answer: 64
 
-6. **What is your waist circumference in centimeters?** (Open-ended)  
+6.  **What is your waist circumference in centimeters?** (Open-ended)\
     Example answer: 85.0
 
-7. **What is your thigh circumference in centimeters?** (Open-ended)  
+7.  **What is your thigh circumference in centimeters?** (Open-ended)\
     Example answer: 62.2
@@
 ### Section 3: Additional Information
+
 8.  **Do you have any medical conditions that may affect body weight (e.g., metabolic disorders)?** (Multiple-choice)
-   - Yes (please specify): ___________  
+    -   Yes (please specify): \_\_\_\_\_\_\_\_\_\_\_\
     -   No
-
 9.  **How frequently do you engage in physical training as part of your military duties?** (Multiple-choice)
-   - Daily  
-   - 3-5 times a week  
-   - 1-2 times a week  
+    -   Daily\
+    -   3-5 times a week\
+    -   1-2 times a week\
     -   Rarely
-
 10. **Do you follow any specific dietary practices or restrictions?** (Multiple-choice)
-    - Yes (please specify): ___________  
+    -   Yes (please specify): \_\_\_\_\_\_\_\_\_\_\_\
     -   No
-
-## Validation and Quality Control
-
-To ensure high-quality responses, several validation and quality control measures would be implemented to minimize bias, enhance reliability, and ensure the accuracy of the collected data:
-
--   Testing Protocols: The survey would be pilot-tested with a small group of personnel to identify potential ambiguities or difficulties in question interpretation.
-Pilot testing helps refine the survey design, ensuring that all questions are clear, relevant, and capable of eliciting accurate responses.
-This step minimizes measurement bias and enhances the reliability of the final data collection instrument.
-
--   Cross-verification: Respondents would provide service branch IDs and ZIP codes for validation against military records.
-This ensures that all participants belong to the intended population (female U.S.
-Army personnel) and reduces the risk of data contamination from ineligible respondents, such as civilians or individuals outside the study's scope.
-
--   Validation Measures: Data would be checked for completion time, with excessively short responses flagged for review.
-Duplicate entries would be identified using IP tracking for online responses.This measure helps reduce bias caused by inattentive or disengaged respondents, ensuring that the data collected reflects thoughtful and accurate input.
 

### 2024-12-02 scripts/00-simulate-data.R

@@ -1,43 +1,0 @@
-#### Preamble ####
-# Purpose: Simulates a dataset of anthropometric and demographic data for analysis
-# Author: 
-# Date: 
-# License: MIT
-
-#### Workspace setup ####
-library(tidyverse)
-library(arrow)
-set.seed(123)  # Set seed for reproducibility
-
-#### Simulate data ####
-
-# Define the number of observations
-n <- 1000
-
-# Simulate data
-simulated_data <- tibble(
-  weight = rnorm(n, mean = 70, sd = 15),                     # Weight in kg (normal distribution)
-  height = rnorm(n, mean = 165, sd = 10),                   # Height in cm
-  waist_circumference = rnorm(n, mean = 85, sd = 15),        # Waist circumference in cm
-  chest_circumference = rnorm(n, mean = 95, sd = 10),        # Chest circumference in cm
-  thigh_circumference = rnorm(n, mean = 55, sd = 7),         # Thigh circumference in cm
-  biceps_circumference = rnorm(n, mean = 30, sd = 5),        # Biceps circumference in cm
-  gender = sample(c("Male", "Female"), size = n, replace = TRUE, prob = c(0.5, 0.5)), # Gender
-  age = sample(18:60, size = n, replace = TRUE),             # Age in years (uniform distribution)
-  ethnicity = sample(
-    c("Asian", "Black", "Hispanic", "White", "Other"),
-    size = n,
-    replace = TRUE,
-    prob = c(0.25, 0.15, 0.2, 0.3, 0.1)                     # Ethnicity probabilities
-  ),
-  component = sample(
-    c("Regular Army", "Reserves", "National Guard"),
-    size = n,
-    replace = TRUE,
-    prob = c(0.6, 0.3, 0.1)                                 # Military component probabilities
-  )
-)
-
-write_parquet(simulated_data, "data/raw-data/simulated_ansur_female_data.parquet")
-write_csv(simulated_data, "data/raw-data/simulated_ansur_female_data.csv")
-

### 2024-12-02 scripts/00-simulate_data.R

@@ -1,0 +1,42 @@
+#### Preamble ####
+# Purpose: Simulates the dataset
+# Author: Huayan Yu
+# Email: huayan.yu@mail.utoronto.ca
+# Date: December 2, 2024
+# License: MIT
+# Pre-requisites: R packages are loaded
+
+#### Workspace setup ####
+library(tidyverse)
+set.seed(123) # Set seed for reproducibility
+
+#### Simulate data ####
+
+# Define the number of observations
+n <- 1000
+
+# Simulate data
+simulated_data <- tibble(
+  weight = rnorm(n, mean = 70, sd = 15), # Weight in kg (normal distribution)
+  height = rnorm(n, mean = 165, sd = 10), # Height in cm
+  waist_circumference = rnorm(n, mean = 85, sd = 15), # Waist circumference in cm
+  chest_circumference = rnorm(n, mean = 95, sd = 10), # Chest circumference in cm
+  thigh_circumference = rnorm(n, mean = 55, sd = 7), # Thigh circumference in cm
+  biceps_circumference = rnorm(n, mean = 30, sd = 5), # Biceps circumference in cm
+  gender = sample(c("Male", "Female"), size = n, replace = TRUE, prob = c(0.5, 0.5)), # Gender
+  age = sample(18:60, size = n, replace = TRUE), # Age in years (uniform distribution)
+  ethnicity = sample(
+    c("Asian", "Black", "Hispanic", "White", "Other"),
+    size = n,
+    replace = TRUE,
+    prob = c(0.25, 0.15, 0.2, 0.3, 0.1) # Ethnicity probabilities
+  ),
+  component = sample(
+    c("Regular Army", "Reserves", "National Guard"),
+    size = n,
+    replace = TRUE,
+    prob = c(0.6, 0.3, 0.1) # Military component probabilities
+  )
+)
+
+write_csv(simulated_data, "data/00-simulated_data/simulated_data.csv")

### 2024-12-02 scripts/01-test_simulate.R

@@ -1,75 +1,0 @@
-#### Preamble ####
-# Purpose: Tests the structure and validity of the simulated anthropometric and demographic dataset
-# Author: 
-# Date: 
-# Contact: 
-# License: MIT
-# Pre-requisites: 
-# - The `tidyverse` and `testthat` packages must be installed and loaded.
-# - The simulated dataset script must have been run to generate `simulated_data`.
-
-#### Workspace setup ####
-library(tidyverse)
-library(testthat)
-
-simulated_data <- read_csv("data/raw-data/simulated_ansur_female_data.csv")
-
-# Ensure `simulated_data` exists
-if (exists("simulated_data")) {
-  message("Test Passed: The simulated dataset was successfully generated.")
-} else {
-  stop("Test Failed: The simulated dataset could not be found.")
-}
-
-#### Test data ####
-
-# Test if the dataset has the correct number of rows and columns
-expected_cols <- c(
-  "weight", "height", "waist_circumference", 
-  "chest_circumference", "thigh_circumference", 
-  "biceps_circumference", "gender", "age", 
-  "ethnicity", "component"
-)
-
-# Test column names
-if (all(colnames(simulated_data) %in% expected_cols)) {
-  message("Test Passed: The dataset contains all expected columns.")
-} else {
-  stop("Test Failed: The dataset does not contain the correct columns.")
-}
-
-# Test the number of rows (expecting 1000)
-if (nrow(simulated_data) == 1000) {
-  message("Test Passed: The dataset contains the expected number of rows (1000).")
-} else {
-  stop("Test Failed: The dataset does not contain the expected number of rows.")
-}
-
-# Test for missing values
-if (all(!is.na(simulated_data))) {
-  message("Test Passed: The dataset contains no missing values.")
-} else {
-  stop("Test Failed: The dataset contains missing values.")
-}
-
-# Test for unique categories in `gender`
-if (length(unique(simulated_data$gender)) == 2) {
-  message("Test Passed: The 'gender' column contains two unique values.")
-} else {
-  stop("Test Failed: The 'gender' column does not contain the expected number of unique values.")
-}
-
-# Test for valid range of ages (should be between 18 and 60)
-if (all(simulated_data$age >= 18 & simulated_data$age <= 60)) {
-  message("Test Passed: The 'age' column contains valid values within the expected range (18-60).")
-} else {
-  stop("Test Failed: The 'age' column contains values outside the expected range.")
-}
[…]

### 2024-12-02 scripts/01-test_simulated_data.R

@@ -1,0 +1,72 @@
+#### Preamble ####
+# Purpose: Test the simulated dataset
+# Author: Huayan Yu
+# Email: huayan.yu@mail.utoronto.ca
+# Date: December 2, 2024
+# License: MIT
+# Pre-requisites: R packages are loaded
+
+#### Workspace setup ####
+library(tidyverse)
+library(testthat)
+
+simulated_data <- read_csv("data/00-simulated_data/simulated_data.csv")
+
+# Ensure `simulated_data` exists
+if (exists("simulated_data")) {
+  message("Test Passed: The simulated dataset was successfully generated.")
+} else {
+  stop("Test Failed: The simulated dataset could not be found.")
+}
+
+#### Test data ####
+
+# Test if the dataset has the correct number of rows and columns
+expected_cols <- c(
+  "weight", "height", "waist_circumference",
+  "chest_circumference", "thigh_circumference",
+  "biceps_circumference", "gender", "age",
+  "ethnicity", "component"
+)
+
+# Test column names
+if (all(colnames(simulated_data) %in% expected_cols)) {
+  message("Test Passed: The dataset contains all expected columns.")
+} else {
+  stop("Test Failed: The dataset does not contain the correct columns.")
+}
+
+# Test the number of rows (expecting 1000)
+if (nrow(simulated_data) == 1000) {
+  message("Test Passed: The dataset contains the expected number of rows (1000).")
+} else {
+  stop("Test Failed: The dataset does not contain the expected number of rows.")
+}
+
+# Test for missing values
+if (all(!is.na(simulated_data))) {
+  message("Test Passed: The dataset contains no missing values.")
+} else {
+  stop("Test Failed: The dataset contains missing values.")
+}
+
+# Test for unique categories in `gender`
+if (length(unique(simulated_data$gender)) == 2) {
+  message("Test Passed: The 'gender' column contains two unique values.")
+} else {
+  stop("Test Failed: The 'gender' column does not contain the expected number of unique values.")
+}
+
+# Test for valid range of ages (should be between 18 and 60)
+if (all(simulated_data$age >= 18 & simulated_data$age <= 60)) {
+  message("Test Passed: The 'age' column contains valid values within the expected range (18-60).")
+} else {
+  stop("Test Failed: The 'age' column contains values outside the expected range.")
+}
+
+# Check for duplicate rows
+if (nrow(simulated_data) == nrow(distinct(simulated_data))) {
[…]

### 2024-12-02 scripts/02-clean_data.R

@@ -1,0 +1,40 @@
+#### Preamble ####
+# Purpose: Cleans the raw dataset for analysis
+# Author: Huayan Yu
+# Email: huayan.yu@mail.utoronto.ca
+# Date: December 2, 2024
+# License: MIT
+# Pre-requisites: Raw data must be downloaded.
+
+#### Workspace setup ####
+library(tidyverse)
+library(janitor) # For clean_names()
+library(tidyr) # For drop_na()
+
+#### Clean data ####
+# Load the raw data
+raw_data <- read_csv("data/01-raw_data/raw_data.csv")
+
+# Clean and prepare the data
+cleaned_data <-
+  raw_data |>
+  janitor::clean_names() |> # Standardize column names
+  select(
+    weightlbs, heightin, waistcircumference,
+    thighcircumference, age, component
+  ) |> # Select relevant variables
+  drop_na() |> # Remove rows with missing values
+  mutate(
+    # Convert character columns to appropriate types if necessary
+    component = as.factor(component),
+    age = as.numeric(age),
+    waistcircumference = waistcircumference / 10,
+    thighcircumference = thighcircumference / 10
+  ) |>
+  rename(
+    waist_circumference = waistcircumference,
+    thigh_circumference = thighcircumference,
+  )
+
+#### Save data ####
+write_parquet(cleaned_data, "data/02-analysis_data/analysis_data.parquet")

### 2024-12-02 scripts/02-download_data.R

@@ -1,24 +1,0 @@
-#### Preamble ####
-# Purpose: Downloads and saves the data 
-# Author:
-# Date:
-# Contact:
-# License: MIT
-# Pre-requisites: None
-
-
-#### Workspace setup ####
-library(tidyverse)
-library(arrow)
-
-
-#### Download data ####
-ansur_female_data <-
-  read_csv(
-    here::here("data/raw-data/ANSUR_II_FEMALE_Public.csv"),
-    show_col_types = FALSE
-  )
-#### Save data ####
-write_parquet(ansur_female_data, "data/raw-data/ansur_female_data.parquet")
-write_csv(ansur_female_data, "data/raw-data/ansur_female_data.csv")
-

### 2024-12-02 scripts/03-test_analysis_data.R

@@ -1,0 +1,47 @@
+#### Preamble ####
+# Purpose: Test the analysis dataset
+# Author: Huayan Yu
+# Email: huayan.yu@mail.utoronto.ca
+# Date: December 2, 2024
+# License: MIT
+# Pre-requisites: R packages are loaded
+
+#### Workspace setup ####
+library(tidyverse)
+library(testthat)
+library(parquet)
+
+analysis_data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
+
+
+# Test if the data was successfully loaded
+if (exists("analysis_data")) {
+  message("Test Passed: The dataset was successfully loaded.")
+} else {
+  stop("Test Failed: The dataset could not be loaded.")
+}
+
+#### Test data ####
+
+# Test if the dataset has the correct number of columns (10 expected)
+
+# Test if there are any missing values in the dataset
+if (all(!is.na(analysis_data))) {
+  message("Test Passed: The dataset contains no missing values.")
+} else {
+  stop("Test Failed: The dataset contains missing values.")
+}
+
+# Test that `component` column contains at least 2 unique values
+if (length(unique(analysis_data$component)) >= 2) {
+  message("Test Passed: The 'component' column contains at least 2 unique values.")
+} else {
+  stop("Test Failed: The 'component' column does not contain at least 2 unique values.")
+}
+
+# Check for duplicate rows
+if (nrow(analysis_data) == nrow(distinct(analysis_data))) {
+  message("Test Passed: There are no duplicate rows in the dataset.")
+} else {
+  stop("Test Failed: The dataset contains duplicate rows.")
+}

### 2024-12-02 scripts/04-exploratory_data_analysis.R

@@ -1,0 +1,40 @@
+#### Preamble ####
+# Purpose: Runs exploratory data analysis using cleaned data
+# Author: Huayan Yu
+# Email: huayan.yu@mail.utoronto.ca
+# Date: December 2, 2024
+# License: MIT
+# Pre-requisites: R packages are loaded
+
+#### Workspace setup ####
+library(tidyverse)
+library(testthat)
+library(arrow)
+
+analysis_data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
+
+ggplot(analysis_data, aes(x = weightlbs)) +
+  geom_histogram(binwidth = 10, fill = "skyblue", color = "black") +
+  labs(title = "Distribution of Weight (lbs)", x = "Weight (lbs)", y = "Count") +
+  theme_minimal()
+
+ggplot(analysis_data, aes(x = heightin, y = weightlbs)) +
+  geom_point(color = "darkblue", alpha = 0.7) +
+  labs(title = "Height vs. Weight", x = "Height (inches)", y = "Weight (lbs)") +
+  theme_minimal()
+
+ggplot(analysis_data, aes(x = component, y = weightlbs, fill = component)) +
+  geom_boxplot() +
+  labs(title = "Weight Distribution by Component", x = "Component", y = "Weight (lbs)") +
+  theme_minimal() +
+  theme(legend.position = "none")
+
+ggplot(analysis_data, aes(x = waist_circumference, y = thigh_circumference)) +
+  geom_point(color = "darkgreen", alpha = 0.7) +
+  labs(title = "Waist vs. Thigh Circumference", x = "Waist Circumference (inches)", y = "Thigh Circumference (inches)") +
+  theme_minimal()
+
+ggplot(analysis_data, aes(x = component)) +
+  geom_bar(fill = "orange", color = "black") +
+  labs(title = "Count of Observations by Component", x = "Component", y = "Count") +
+  theme_minimal()

### 2024-12-02 scripts/04-test_analysis.R

@@ -1,50 +1,0 @@
-#### Preamble ####
-# Purpose: Tests the structure and validity of the cleaned ANSUR II Female dataset
-# Author: 
-# Date: 
-# Contact:
-# License: MIT
-# Pre-requisites: 
-# - The `tidyverse` and `testthat` packages must be installed and loaded.
-# - 03-clean_data.R must have been run.
-# Any other information needed? Make sure you are in the correct R project directory.
-
-#### Workspace setup ####
-library(tidyverse)
-library(testthat)
-
-analysis_data <- read_csv("data/analysis-data/ansur_female_data.csv")
-
-
-# Test if the data was successfully loaded
-if (exists("analysis_data")) {
-  message("Test Passed: The dataset was successfully loaded.")
-} else {
-  stop("Test Failed: The dataset could not be loaded.")
-}
-
-#### Test data ####
-
-# Test if the dataset has the correct number of columns (10 expected)
-
-# Test if there are any missing values in the dataset
-if (all(!is.na(analysis_data))) {
-  message("Test Passed: The dataset contains no missing values.")
-} else {
-  stop("Test Failed: The dataset contains missing values.")
-}
-
-# Test that `component` column contains at least 2 unique values
-if (length(unique(analysis_data$component)) >= 2) {
-  message("Test Passed: The 'component' column contains at least 2 unique values.")
-} else {
-  stop("Test Failed: The 'component' column does not contain at least 2 unique values.")
-}
-
-# Check for duplicate rows
-if (nrow(analysis_data) == nrow(distinct(analysis_data))) {
-  message("Test Passed: There are no duplicate rows in the dataset.")
-} else {
-  stop("Test Failed: The dataset contains duplicate rows.")
-}
-

### 2024-12-02 scripts/05-model.R

@@ -1,9 +1,10 @@
 #### Preamble ####
-# Purpose: Create Bayesian regression model on cleaned ANSUR II Female data
-# Author:
-# Date: 
+# Purpose: Create Bayesian regression model on cleaned data
+# Author: Huayan Yu
+# Email: huayan.yu@mail.utoronto.ca
+# Date: December 2, 2024
 # License: MIT
-# Pre-requisites: None
+# Pre-requisites: R packages are loaded
 
 #### Workspace setup ####
 library(rstanarm) # Load the rstanarm package for Bayesian modeling
@@ -11,19 +12,13 @@ library(arrow) # Load the arrow package to read Parquet files
 library(dplyr)
 
 #### Read data ####
-cleaned_ansur_female_data <- read_parquet("data/analysis-data/ansur_female_data.parquet")
+analysis_data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
 
 #### Model data ####
-
-# Random sampling if needed
-set.seed(123)
-sampled_ansur_data <- cleaned_ansur_female_data %>%
-  sample_n(1000) 
-
 # Build a Bayesian regression model using stan_glm
-ansur_bayesian_model <- stan_glm(
+bayesian_model <- stan_glm(
   formula = weightlbs ~ heightin + waist_circumference + thigh_circumference + age + component,
-  data = sampled_ansur_data,
+  data = analysis_data,
   family = gaussian(), # Specify a Gaussian family for continuous outcomes
   prior = normal(0, 1), # Use a normal prior with mean 0 and SD 1
   prior_intercept = normal(0, 1), # Use a normal prior for the intercept
@@ -32,7 +27,6 @@ ansur_bayesian_model <- stan_glm(
 
 #### Save model ####
 saveRDS(
-  ansur_bayesian_model,
-  file = "models/ansur_bayesian_model.rds"
+  bayesian_model,
+  file = "models/bayesian_model.rds"
 )
-

### 2024-12-03 paper/paper.qmd
Update paper.qmd

@@
 
-The ANSUR II dataset provides comprehensive anthropometric and demographic data for 1,986 female U.S [@ansurII_female].
+The ANSUR II dataset provides comprehensive anthropometric and demographic data for 1,986 female U.S [@ANSURII_2012].
 Army personnel, collected using standardized protocols to ensure accuracy.
@@
 
+All the data analysis was done through R (R Core Team 2023) with the aid of various packages in the R programming language.
 The `tidyverse` package [@tidyverse] was used to streamline the entire process of data manipulation, transformation, and visualization, ensuring consistency, efficiency, and flexibility throughout the analysis.

### 2024-12-03 scripts/00-simulate_data.R
Update 00-simulate_data.R

@@ -16,27 +16,49 @@ set.seed(123) # Set seed for reproducibility
 n <- 1000
 
 # Simulate data
+set.seed(123) # Ensure reproducibility
+
 simulated_data <- tibble(
-  weight = rnorm(n, mean = 70, sd = 15), # Weight in kg (normal distribution)
+  # Weight and Waist Circumference with a correlation
+  weight = rnorm(n, mean = 70, sd = 15), # Weight in kg
+  waist_circumference = weight * 0.4 + rnorm(n, mean = 0, sd = 5), # Correlation with weight
+  
+  # Height independent of weight/waist
   height = rnorm(n, mean = 165, sd = 10), # Height in cm
-  waist_circumference = rnorm(n, mean = 85, sd = 15), # Waist circumference in cm
-  chest_circumference = rnorm(n, mean = 95, sd = 10), # Chest circumference in cm
-  thigh_circumference = rnorm(n, mean = 55, sd = 7), # Thigh circumference in cm
-  biceps_circumference = rnorm(n, mean = 30, sd = 5), # Biceps circumference in cm
-  gender = sample(c("Male", "Female"), size = n, replace = TRUE, prob = c(0.5, 0.5)), # Gender
-  age = sample(18:60, size = n, replace = TRUE), # Age in years (uniform distribution)
+  
+  # Chest circumference proportional to height, with some noise
+  chest_circumference = height * 0.55 + rnorm(n, mean = 0, sd = 7), # Adding interaction
+  
+  # Thigh circumference weakly proportional to height
+  thigh_circumference = height * 0.33 + rnorm(n, mean = 0, sd = 3),
+  
+  # Gender-based biceps circumference
+  gender = sample(c("Male", "Female"), size = n, replace = TRUE, prob = c(0.5, 0.5)),
+  biceps_circumference = if_else(
+    gender == "Male",
+    rnorm(n, mean = 32, sd = 5), # Males have a higher mean
+    rnorm(n, mean = 28, sd = 4)  # Females have a lower mean
+  ),
+  
+  # Age uniformly distributed
+  age = sample(18:60, size = n, replace = TRUE),
+  
+  # Ethnicity probabilities
   ethnicity = sample(
     c("Asian", "Black", "Hispanic", "White", "Other"),
     size = n,
     replace = TRUE,
-    prob = c(0.25, 0.15, 0.2, 0.3, 0.1) # Ethnicity probabilities
[…]

### 2024-12-04 scripts/00-simulate_data.R
Update 00-simulate_data.R

@@ -16,8 +16,6 @@ set.seed(123) # Set seed for reproducibility
 n <- 1000
 
 # Simulate data
-set.seed(123) # Ensure reproducibility
-
 simulated_data <- tibble(
   # Weight and Waist Circumference with a correlation
   weight = rnorm(n, mean = 70, sd = 15), # Weight in kg

### 2024-12-04 scripts/00-simulate_data.R
Update 00-simulate_data.R

@@ -2,7 +2,7 @@
 # Purpose: Simulates the dataset
 # Author: Huayan Yu
 # Email: huayan.yu@mail.utoronto.ca
-# Date: December 2, 2024
+# Date: December 3, 2024
 # License: MIT
 # Pre-requisites: R packages are loaded
 
@@ -17,46 +17,26 @@ n <- 1000
 
 # Simulate data
 simulated_data <- tibble(
-  # Weight and Waist Circumference with a correlation
-  weight = rnorm(n, mean = 70, sd = 15), # Weight in kg
-  waist_circumference = weight * 0.4 + rnorm(n, mean = 0, sd = 5), # Correlation with weight
-  
-  # Height independent of weight/waist
+  weight = rnorm(n, mean = 70, sd = 15), # Weight in kg (normal distribution)
   height = rnorm(n, mean = 165, sd = 10), # Height in cm
-  
-  # Chest circumference proportional to height, with some noise
-  chest_circumference = height * 0.55 + rnorm(n, mean = 0, sd = 7), # Adding interaction
-  
-  # Thigh circumference weakly proportional to height
-  thigh_circumference = height * 0.33 + rnorm(n, mean = 0, sd = 3),
-  
-  # Gender-based biceps circumference
-  gender = sample(c("Male", "Female"), size = n, replace = TRUE, prob = c(0.5, 0.5)),
-  biceps_circumference = if_else(
-    gender == "Male",
-    rnorm(n, mean = 32, sd = 5), # Males have a higher mean
-    rnorm(n, mean = 28, sd = 4)  # Females have a lower mean
-  ),
-  
-  # Age uniformly distributed
-  age = sample(18:60, size = n, replace = TRUE),
-  
-  # Ethnicity probabilities
+  waist_circumference = rnorm(n, mean = 85, sd = 15), # Waist circumference in cm
+  chest_circumference = rnorm(n, mean = 95, sd = 10), # Chest circumference in cm
+  thigh_circumference = rnorm(n, mean = 55, sd = 7), # Thigh circumference in cm
+  biceps_circumference = rnorm(n, mean = 30, sd = 5), # Biceps circumference in cm
+  gender = sample(c("Male", "Female"), size = n, replace = TRUE, prob = c(0.5, 0.5)), # Gender
+  age = sample(18:60, size = n, replace = TRUE), # Age in years (uniform distribution)
   ethnicity = sample(
[…]

### 2024-12-04 paper/paper.qmd
rendered paper
added model comparison

@@
 
-All the data analysis was done through R (R Core Team 2023) with the aid of various packages in the R programming language.
+All the data analysis was done through `R` with the aid of various packages in the `R` programming language [@citeR].
 The `tidyverse` package [@tidyverse] was used to streamline the entire process of data manipulation, transformation, and visualization, ensuring consistency, efficiency, and flexibility throughout the analysis.
@@
 
-## Reflecting Data Features in Model Design
+## Predictors Choice
 
@@
 
-## Justification for the Priors and Model Choice
+## Model Justification
 
@@
 
-A frequentist linear regression model was also considered for its simplicity and interpretability; however, it does not provide posterior distributions or credible intervals, which are essential for quantifying uncertainty in this study.
+A Frequentist linear regression model was also initially considered for its simplicity and interpretability; however, it does not provide posterior distributions or credible intervals, which are essential for quantifying uncertainty in this study.
 By contrast, the Bayesian regression framework provides probabilistic estimates, enabling uncertainty quantification and credible intervals for the coefficients.
 This approach aligns well with the study's objectives, where understanding the relative influence of predictors on body weight requires a robust and interpretable model.
-The rstanarm package was chosen for its efficient handling of Bayesian inference and built-in diagnostics, ensuring rigorous validation.
+The `rstanarm` package was chosen for its efficient handling of Bayesian inference and built-in diagnostics, ensuring rigorous validation.
 The Gaussian likelihood function complements the continuous nature of the outcome variable (body weight), and the model structure strikes a balance between simplicity and capturing key relationships in the data.
 
+## Model Selection
+
+The model selection process involved building and comparing two Bayesian regression models using the analysis data: a full model with all predictors and a reduced model with only age and component as predictors.
+The data was split into training (80%) and testing (20%) subsets for model evaluation.
+Both models were fit using the stan_glm function, and predictions were made on the test set.
+The models were evaluated using Root Mean Square Error (RMSE) as a metric of predictive performance.
+The results showed that the full model had a slightly lower RMSE (133.16) compared to the reduced model (134.49), indicating that the additional predictors in the full model improved its predictive accuracy, albeit marginally.
+
 # Results {#sec-result}
-
-## Model Justification
 

### 2024-12-04 scripts/05-model.R

@@ -15,9 +15,19 @@ library(dplyr)
 analysis_data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
 
 #### Model data ####
-# Build a Bayesian regression model using stan_glm
+# Build a Bayesian regression model 
 bayesian_model <- stan_glm(
   formula = weightlbs ~ heightin + waist_circumference + thigh_circumference + age + component,
+  data = analysis_data,
+  family = gaussian(), # Specify a Gaussian family for continuous outcomes
+  prior = normal(0, 1), # Use a normal prior with mean 0 and SD 1
+  prior_intercept = normal(0, 1), # Use a normal prior for the intercept
+  seed = 123 # Set a random seed for reproducibility
+)
+
+# Build a reduced model 
+bayesian_model1 <- stan_glm(
+  formula = weightlbs ~ age + component,
   data = analysis_data,
   family = gaussian(), # Specify a Gaussian family for continuous outcomes
   prior = normal(0, 1), # Use a normal prior with mean 0 and SD 1
@@ -30,3 +40,38 @@ saveRDS(
   bayesian_model,
   file = "models/bayesian_model.rds"
 )
+
+saveRDS(
+  bayesian_model1,
+  file = "models/bayesian_model_reduced.rds"
+)
+
+#### Model Selection ####
+# Train-test split
+set.seed(123)  # For reproducibility
+train_indices <- sample(1:nrow(analysis_data), size = 0.8 * nrow(analysis_data))
+train_data <- analysis_data[train_indices, ]
+test_data <- analysis_data[-train_indices, ]
+
+# Evaluate models
+# Function to calculate RMSE
+calculate_rmse <- function(actual, predicted) {
+  sqrt(mean((actual - predicted)^2))
+}
+
+# Predictions and evaluation for full model
+bayesian_preds <- posterior_predict(bayesian_model, newdata = test_data)
+bayesian_preds_mean <- apply(bayesian_preds, 2, mean)  # Mean of posterior predictions
+bayesian_rmse <- calculate_rmse(test_data$weightlbs, bayesian_preds_mean)
+
+# Predictions and evaluation for reduced model
+bayesian_preds1 <- posterior_predict(bayesian_model1, newdata = test_data)
+bayesian_preds1_mean <- apply(bayesian_preds1, 2, mean)  # Mean of posterior predictions
[…]

### 2024-12-11 paper/paper.qmd
update introduction section

@@
 Army, maintaining optimal weight is crucial to meet fitness standards, reduce injury risks, and ensure operational efficiency.
+Soldiers who are overweight or underweight may face challenges in meeting the physical demands required for combat readiness, logistical tasks, and high-intensity training.
+Therefore, understanding the factors that influence body weight is vital for designing effective health and fitness programs that enhance both individual and unit performance.
 While extensive anthropometric and demographic data exist, limited research explores the combined influence of these factors on body weight, particularly among female soldiers [@gordon2014].
+This gap in research limits the ability to create targeted interventions and policies that account for the unique physiological and demographic characteristics of female service members.
 
@@
 Army Anthropometric Survey (ANSUR II) Female Dataset, which includes precise anthropometric and demographic measurements of female personnel.
-Data collection utilized standardized instruments such as stadiometers and calipers, ensuring high reliability and consistency [@hotzman2011; @paquette2009].
-Key variables, including height, waist circumference, and thigh circumference, were measured to assess body composition, while demographic factors such as age, ethnicity, and military component were cross-validated with administrative records [@gordon2014].
+The ANSUR II dataset is a comprehensive resource, providing detailed measurements that facilitate nuanced analyses of body composition and weight determinants.
+Data collection utilized standardized instruments such as stadiometers, calipers, and body scales, ensuring high reliability and consistency in measurements [@hotzman2011; @paquette2009].
+These tools minimize measurement errors and ensure comparability across different participants and testing locations.
+For instance, stadiometers ensured accurate height measurements, while calipers provided precise assessments of skinfold thickness, contributing to a more detailed understanding of body fat distribution.
+
+Key anthropometric variables measured in this study include height, waist circumference, hip circumference, thigh circumference, and body mass index (BMI).
+These variables are critical in understanding body composition, as they provide insight into fat distribution, muscle mass, and overall body structure.
+Height, for example, is a fundamental determinant of body weight, as taller individuals typically possess greater lean mass and bone density.
+Waist circumference is an important indicator of central adiposity, which has been linked to various health risks, including metabolic syndrome and cardiovascular disease [@gordon2014].
+Additionally, thigh circumference reflects lower body muscle mass, which is essential for tasks requiring strength and endurance.
+These anthropometric measurements are complemented by demographic factors such as age, ethnicity, rank, and military component (active duty, reserve, or National Guard), which were cross-validated with administrative records to ensure accuracy and completeness [@gordon2014].
 
@@
 Army personnel.
-Specifically, it quantifies how variations in measurements such as height and waist circumference, alongside demographic factors like age and ethnicity, contribute to body weight.
-The goal is to identify significant predictors and develop a robust predictive model that can inform health monitoring, tailored fitness programs, and ergonomic equipment design.
+Specifically, the study seeks to quantify how variations in measurements such as height, waist circumference, hip circumference, and thigh circumference, alongside demographic factors like age, ethnicity, and military component, contribute to body weight.
+By incorporating multiple predictors, the study aims to capture the complexity of factors influencing body weight and provide a more comprehensive understanding of weight dynamics in female soldiers.
+The goal is to identify the most significant predictors and develop a robust predictive model that can inform health monitoring, tailored fitness programs, and ergonomic equipment design.
+
+Developing such a model has several practical applications.
+For instance, personalized fitness programs can be designed based on an individual's anthropometric and demographic profile, ensuring more effective weight management and injury prevention.
+These programs can address specific needs related to body composition, such as increasing muscle mass or reducing body fat, depending on the soldier's role and physical requirements.
+Furthermore, insights from the predictive model can aid in the design of military gear and equipment that better fits the diverse body shapes and sizes of female soldiers, thereby enhancing comfort, mobility, and performance [@opendesignlab2018].
+Properly fitted equipment reduces the risk of musculoskeletal injuries and improves operational efficiency, particularly during physically demanding tasks [@paquette2009].
 
 Preliminary findings underscore the strong predictive power of anthropometric variables in determining body weight, with demographic factors serving as additional contributors.
-These insights support the development of personalized fitness interventions, improved health outcomes, and the optimization of military gear to enhance operational readiness [@opendesignlab2018; @paquette2009].
+For example, height and waist circumference exhibit significant positive correlations with body weight, indicating that both structural and compositional factors play crucial roles.
+Age and ethnicity further modulate these relationships, reflecting variations in body composition and metabolic processes across different demographic groups.
+These insights support the development of personalized fitness interventions that are sensitive to both physical and demographic characteristics.
+Additionally, the findings contribute to improved health outcomes by identifying soldiers at higher risk of weight-related health issues and facilitating early intervention [@hotzman2011; @paquette2009].
+
+By integrating anthropometric and demographic data, this study not only enhances our understanding of weight determinants among female soldiers but also provides actionable recommendations for optimizing health and performance.
+This approach aligns with broader efforts to improve soldier readiness, reduce injury rates, and ensure that military personnel are equipped to meet the physical challenges of their roles.
+Ultimately, these insights contribute to the overarching goal of maintaining a fit, healthy, and operationally ready force capable of responding to the diverse demands of modern military service [@opendesignlab2018].
 

### 2024-12-11 paper/paper.qmd
update discussion section

@@
 The results emphasize the significant role of anthropometric variables, particularly waist circumference and thigh circumference, as strong predictors of body weight.
-These findings align with previous research, which identify waist circumference as a key indicator of central adiposity and overall body composition [@heymsfield2015], and studies linking thigh circumference to lower body strength and fat distribution [@snijder2005].
-These measurements are critical in the military context, where body composition impacts physical performance and injury risk.
-The observed positive associations reinforce the importance of these variables in health monitoring, fitness interventions, and ergonomic considerations for military equipment design.
+These findings align with previous research identifying waist circumference as a key indicator of central adiposity and overall body composition [@heymsfield2015].
+Central adiposity is known to be associated with higher risks of cardiovascular disease, metabolic disorders, and reduced physical performance, making it a critical measurement for monitoring the health of military personnel.
+In physically demanding contexts such as military service, excessive central adiposity can impair mobility, endurance, and the ability to perform tasks under pressure.
+
+Similarly, thigh circumference is a valuable indicator of lower body strength and fat distribution, as supported by studies linking larger thigh circumference to greater muscle mass and reduced injury risk [@snijder2005].
+In the military context, strong lower body muscles are essential for activities such as marching, running, lifting heavy equipment, and maintaining stability during combat operations.
+The observed positive associations between thigh circumference and body weight reinforce the importance of maintaining lower body muscle mass to support physical performance and reduce the risk of musculoskeletal injuries.
 
 Although height showed a weaker association with body weight, its inclusion remains biologically plausible.
-Taller individuals typically exhibit larger skeletal structures and greater overall body mass.
-This finding is consistent with literature suggesting that height, while less variable than other anthropometric measures, contributes to baseline estimations of body weight.
+Taller individuals typically exhibit larger skeletal structures, greater lean mass, and increased overall body mass.
+This finding is consistent with literature suggesting that while height is less variable than other anthropometric measures, it contributes to baseline estimations of body weight.
+In practical terms, height serves as an important reference point when assessing body composition, ensuring that weight management programs account for natural variations in skeletal size and proportionality.
+
 These results underscore the nuanced relationships between body composition and demographic factors, offering a foundation for targeted health interventions within military populations.
+For example, female soldiers with higher waist circumference might benefit from interventions focused on core strength and fat reduction, while those with lower thigh circumference might require programs aimed at building lower body muscle mass.
+Such tailored approaches can enhance fitness outcomes and operational readiness, ensuring that all soldiers meet the physical demands of their roles.
 
@@
 For instance, the findings could guide the development of tailored fitness programs to address central adiposity (waist circumference) and muscle mass (thigh circumference), enhancing operational readiness and reducing injury risks.
+In addition to fitness programs, these insights can inform the design of ergonomic military gear and protective equipment that better fits the diverse body shapes and sizes of female soldiers.
+Properly fitted equipment can improve mobility, comfort, and performance, reducing the likelihood of injuries caused by ill-fitting gear.
+
 These insights align with broader public health objectives, such as the World Health Organization's emphasis on preventing obesity-related conditions through effective weight management strategies.
+The identification of key anthropometric predictors of body weight can support initiatives aimed at promoting healthy body composition and preventing chronic diseases.
+For example, routine monitoring of waist and thigh circumference in both military and civilian populations can serve as an early indicator of health risks, prompting timely interventions and lifestyle modifications.
 
 The use of Bayesian regression models in this study further demonstrates the flexibility and interpretability of these methods for investigating complex relationships between biological and demographic factors.
-Bayesian approaches have been increasingly recognized in health research for their ability to incorporate prior knowledge and quantify uncertainty, making them well-suited for studies involving multifactorial predictors.
+Bayesian approaches are particularly advantageous in health research due to their ability to incorporate prior knowledge, quantify uncertainty, and provide probabilistic estimates.
+These features make Bayesian models well-suited for studies involving multifactorial predictors and datasets with inherent variability.
+For instance, Bayesian frameworks can accommodate uncertainty in measurement data, ensuring robust and reliable estimates even when sample sizes are limited.
 
-Looking ahead, integrating more comprehensive datasets and leveraging advanced analytical techniques, such as machine learning or longitudinal modeling, could deepen our understanding of body weight determinants.
-For example, algorithms trained on diverse datasets could identify non-linear patterns and interactions that traditional regression models might overlook.
-Such efforts would not only enhance health outcomes for military personnel but also contribute to broader efforts to improve public health, workplace ergonomics, and fitness standards across diverse populations.
+Moreover, Bayesian methods facilitate the exploration of posterior distributions and credible intervals, providing a clearer understanding of the relationships between predictors and outcomes.
+This level of detail is invaluable for developing evidence-based policies and interventions that account for variability across different subgroups.
+For example, Bayesian models can reveal how the relationship between waist circumference and body weight differs by age group, ethnicity, or military component, allowing for more targeted and effective strategies.
 

### 2024-12-11 scripts/00-simulate_data.R
update all scripts

@@ -4,7 +4,7 @@
 # Email: huayan.yu@mail.utoronto.ca
 # Date: December 3, 2024
 # License: MIT
-# Pre-requisites: R packages are loaded
+# Pre-requisites: R package `tidyverse` are loaded
 
 #### Workspace setup ####
 library(tidyverse)
@@ -15,14 +15,9 @@ set.seed(123) # Set seed for reproducibility
 # Define the number of observations
 n <- 1000
 
-# Simulate data
+# Simulate data with dependencies
 simulated_data <- tibble(
-  weight = rnorm(n, mean = 70, sd = 15), # Weight in kg (normal distribution)
   height = rnorm(n, mean = 165, sd = 10), # Height in cm
-  waist_circumference = rnorm(n, mean = 85, sd = 15), # Waist circumference in cm
-  chest_circumference = rnorm(n, mean = 95, sd = 10), # Chest circumference in cm
-  thigh_circumference = rnorm(n, mean = 55, sd = 7), # Thigh circumference in cm
-  biceps_circumference = rnorm(n, mean = 30, sd = 5), # Biceps circumference in cm
   gender = sample(c("Male", "Female"), size = n, replace = TRUE, prob = c(0.5, 0.5)), # Gender
   age = sample(18:60, size = n, replace = TRUE), # Age in years (uniform distribution)
   ethnicity = sample(
@@ -36,7 +31,17 @@ simulated_data <- tibble(
     size = n,
     replace = TRUE,
     prob = c(0.6, 0.3, 0.1) # Military component probabilities
-  )
+  ),
+  # Weight depends on height and gender
+  weight = rnorm(n, mean = 70 + 0.3 * (height - 165) + ifelse(gender == "Male", 5, 0), sd = 15),
+  # Waist circumference depends on weight and gender
+  waist_circumference = rnorm(n, mean = 85 + 0.4 * (weight - 70) + ifelse(gender == "Male", 5, -3), sd = 10),
+  # Chest circumference depends on weight and gender
+  chest_circumference = rnorm(n, mean = 95 + 0.3 * (weight - 70) + ifelse(gender == "Male", 5, -2), sd = 10),
+  # Thigh circumference depends on weight
+  thigh_circumference = rnorm(n, mean = 55 + 0.2 * (weight - 70), sd = 7),
+  # Biceps circumference depends on gender and weight
[…]

### 2024-12-11 scripts/01-test_simulated_data.R

@@ -4,7 +4,7 @@
 # Email: huayan.yu@mail.utoronto.ca
 # Date: December 2, 2024
 # License: MIT
-# Pre-requisites: R packages are loaded
+# Pre-requisites: R packages `tidyverse` and `testthat` are loaded
 
 #### Workspace setup ####
 library(tidyverse)
@@ -21,7 +21,7 @@ if (exists("simulated_data")) {
 
 #### Test data ####
 
-# Test if the dataset has the correct number of rows and columns
+# Define the expected columns
 expected_cols <- c(
   "weight", "height", "waist_circumference",
   "chest_circumference", "thigh_circumference",
@@ -29,44 +29,38 @@ expected_cols <- c(
   "ethnicity", "component"
 )
 
-# Test column names
-if (all(colnames(simulated_data) %in% expected_cols)) {
-  message("Test Passed: The dataset contains all expected columns.")
-} else {
-  stop("Test Failed: The dataset does not contain the correct columns.")
-}
+# Test if the dataset contains all expected columns
+test_that("The dataset contains all expected columns", {
+  expect_true(all(colnames(simulated_data) %in% expected_cols),
+              info = "The dataset does not contain the correct columns.")
+})
 
-# Test the number of rows (expecting 1000)
-if (nrow(simulated_data) == 1000) {
-  message("Test Passed: The dataset contains the expected number of rows (1000).")
-} else {
-  stop("Test Failed: The dataset does not contain the expected number of rows.")
-}
+# Test if the dataset has the expected number of rows (1000)
+test_that("The dataset contains the expected number of rows", {
+  expect_equal(nrow(simulated_data), 1000,
+               info = "The dataset does not contain the expected number of rows (1000).")
+})
 
-# Test for missing values
-if (all(!is.na(simulated_data))) {
-  message("Test Passed: The dataset contains no missing values.")
-} else {
-  stop("Test Failed: The dataset contains missing values.")
-}
+# Test for no missing values in the dataset
+test_that("The dataset contains no missing values", {
+  expect_true(all(!is.na(simulated_data)),
+              info = "The dataset contains missing values.")
+})
 
-# Test for unique categories in `gender`
-if (length(unique(simulated_data$gender)) == 2) {
-  message("Test Passed: The 'gender' column contains two unique values.")
-} else {
-  stop("Test Failed: The 'gender' column does not contain the expected number of unique values.")
-}
+# Test if the 'gender' column contains exactly two unique values
[…]

### 2024-12-11 scripts/02-clean_data.R

@@ -4,7 +4,7 @@
 # Email: huayan.yu@mail.utoronto.ca
 # Date: December 2, 2024
 # License: MIT
-# Pre-requisites: Raw data must be downloaded.
+# Pre-requisites: Raw data must be downloaded and R packages `tidyverse`, `janitor`, `tidyr` are loaded.
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-12-11 scripts/03-test_analysis_data.R

@@ -4,15 +4,14 @@
 # Email: huayan.yu@mail.utoronto.ca
 # Date: December 2, 2024
 # License: MIT
-# Pre-requisites: R packages are loaded
+# Pre-requisites: R packages `tidyverse`, `testthat` and `arrow` are loaded
 
 #### Workspace setup ####
 library(tidyverse)
 library(testthat)
-library(parquet)
+library(arrow)
 
 analysis_data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
-
 
 # Test if the data was successfully loaded
 if (exists("analysis_data")) {
@@ -23,25 +22,38 @@ if (exists("analysis_data")) {
 
 #### Test data ####
 
-# Test if the dataset has the correct number of columns (10 expected)
+# Define the expected columns
+expected_cols <- c(
+  "weightlbs", "heightin", "waist_circumference",
+  "thigh_circumference", "age", "component"
+)
 
-# Test if there are any missing values in the dataset
-if (all(!is.na(analysis_data))) {
-  message("Test Passed: The dataset contains no missing values.")
-} else {
-  stop("Test Failed: The dataset contains missing values.")
-}
+# Test if the dataset contains all expected columns
+test_that("The dataset contains all expected columns", {
+  expect_true(all(colnames(analysis_data) %in% expected_cols),
+              info = "The dataset does not contain the correct columns.")
+})
 
-# Test that `component` column contains at least 2 unique values
-if (length(unique(analysis_data$component)) >= 2) {
-  message("Test Passed: The 'component' column contains at least 2 unique values.")
-} else {
-  stop("Test Failed: The 'component' column does not contain at least 2 unique values.")
-}
+# Test if the dataset has the expected number of rows (1986)
+test_that("The dataset contains the expected number of rows", {
+  expect_equal(nrow(analysis_data), 1986,
+               info = "The dataset does not contain the expected number of rows (1986).")
+})
 
-# Check for duplicate rows
-if (nrow(analysis_data) == nrow(distinct(analysis_data))) {
-  message("Test Passed: There are no duplicate rows in the dataset.")
-} else {
-  stop("Test Failed: The dataset contains duplicate rows.")
-}
+# Test for no missing values in the dataset
+test_that("The dataset contains no missing values", {
+  expect_true(all(!is.na(analysis_data)),
+              info = "The dataset contains missing values.")
+})
+
+# Test if the 'age' column contains values within the range 17 to 60
[…]

### 2024-12-11 scripts/04-exploratory_data_analysis.R

@@ -4,11 +4,10 @@
 # Email: huayan.yu@mail.utoronto.ca
 # Date: December 2, 2024
 # License: MIT
-# Pre-requisites: R packages are loaded
+# Pre-requisites: R packages `tidyverse` and `arrow` are loaded
 
 #### Workspace setup ####
 library(tidyverse)
-library(testthat)
 library(arrow)
 
 analysis_data <- read_parquet("data/02-analysis_data/analysis_data.parquet")

### 2024-12-11 scripts/05-model.R

@@ -4,11 +4,11 @@
 # Email: huayan.yu@mail.utoronto.ca
 # Date: December 2, 2024
 # License: MIT
-# Pre-requisites: R packages are loaded
+# Pre-requisites: R packages `dplyr`, `rstanarm`, and `arrow` loaded
 
 #### Workspace setup ####
-library(rstanarm) # Load the rstanarm package for Bayesian modeling
-library(arrow) # Load the arrow package to read Parquet files
+library(rstanarm) 
+library(arrow) 
 library(dplyr)
 
 #### Read data ####

### 2024-12-11 paper/paper.qmd
Update paper.qmd
Refine wording for clarity and precision

--- 2024-12-04 paper/paper.qmd
@@
 
-Body weight plays a critical role in physical performance, health, and operational readiness, particularly in demanding professions such as military service.
+Body weight significantly impacts physical performance, health, and operational readiness, particularly in demanding professions such as military service.
 For the U.S.
-Army, maintaining optimal weight is crucial to meet fitness standards, reduce injury risks, and ensure operational efficiency.
+Army, maintaining optimal weight is essential to meet fitness standards, reduce injury risks, and ensure operational efficiency.
 While extensive anthropometric and demographic data exist, limited research explores the combined influence of these factors on body weight, particularly among female soldiers [@gordon2014].
 
-This study addresses this gap by leveraging the 2012 U.S.
-Army Anthropometric Survey (ANSUR II) Female Dataset, which includes precise anthropometric and demographic measurements of female personnel.
-Data collection utilized standardized instruments such as stadiometers and calipers, ensuring high reliability and consistency [@hotzman2011; @paquette2009].
+This study seeks to address the limited understanding of this issue by utilizing the 2012 U.S.
+Army Anthropometric Survey (ANSUR II) Female Dataset, which provides detailed anthropometric and demographic measurements of female personnel.
+Data collection was conducted using standardized instruments such as stadiometers and calipers, ensuring high reliability and consistency [@hotzman2011; @paquette2009].
 Key variables, including height, waist circumference, and thigh circumference, were measured to assess body composition, while demographic factors such as age, ethnicity, and military component were cross-validated with administrative records [@gordon2014].
@@
 Army personnel.
-Specifically, it quantifies how variations in measurements such as height and waist circumference, alongside demographic factors like age and ethnicity, contribute to body weight.
-The goal is to identify significant predictors and develop a robust predictive model that can inform health monitoring, tailored fitness programs, and ergonomic equipment design.
+Specifically, it examines how variations in measurements such as height and waist circumference, alongside demographic factors like age and ethnicity, influence body weight.
+The goal is to identify significant predictors and develop a reliable predictive model that can guide health monitoring, personalized fitness programs, and ergonomic equipment design.
 
 Preliminary findings underscore the strong predictive power of anthropometric variables in determining body weight, with demographic factors serving as additional contributors.
-These insights support the development of personalized fitness interventions, improved health outcomes, and the optimization of military gear to enhance operational readiness [@opendesignlab2018; @paquette2009].
+These results support the development of personalized fitness interventions, improved health outcomes, and the optimization of military gear to enhance operational readiness [@opendesignlab2018; @paquette2009].
 
@@
 Army personnel, collected using standardized protocols to ensure accuracy.
-Unlike civilian datasets, it uniquely addresses the physical demands and characteristics of military personnel, offering rare insights into factors like fitness, injury risk, and gear design [@hotzman2011].
+Unlike civilian datasets, it uniquely addresses the physical demands and characteristics of military personnel, offering valuable information on factors like fitness, injury risk, and gear design [@hotzman2011].
 Its specificity makes it a vital resource for understanding and improving the health, safety, and operational readiness of female soldiers [@paquette2009].
@@
 Although other publicly available datasets focus on anthropometric measurements, they are typically centered on civilian populations or mixed-gender samples, which do not capture the unique physical demands and requirements of military personnel.
-Civilian datasets often lack the granularity necessary to account for the operational and performance-based contexts of military service, where precise body measurements can impact everything from uniform design to load-bearing capacity and overall readiness.
-Moreover, military-specific datasets are rarely accessible to researchers due to stringent security and privacy concerns, creating a significant gap in publicly available data for this specialized group.
+Civilian datasets often lack the detail necessary to account for the operational and performance-based contexts of military service, where precise body measurements can influence uniform design, load-bearing capacity, and overall readiness.
+Furthermore, military-specific datasets are rarely accessible to researchers due to stringent security and privacy concerns, limiting publicly available data for this specialized group.
 
-The ANSUR II dataset bridges this gap by providing one of the most comprehensive sources of anthropometric and demographic data specific to female military personnel.
-This specificity is crucial for understanding the physical characteristics and needs of female soldiers, who face unique challenges compared to their male counterparts.
-The dataset's depth allows researchers to analyze relationships between body dimensions and factors such as physical performance, injury risk, and operational readiness.
-Furthermore, it offers valuable insights for developing tailored fitness programs, improving gear design, and enhancing overall health and safety standards in military contexts.
+The ANSUR II dataset stands out as one of the most detailed and specific sources of anthropometric and demographic data focused on female military personnel.
+This specificity is essential for understanding the physical characteristics and needs of female soldiers, who face unique challenges compared to their male counterparts.
+The dataset's depth enables researchers to analyze relationships between body dimensions and factors such as physical performance, injury risk, and operational readiness.
+Furthermore, it provides essential information for developing tailored fitness programs, improving gear design, and enhancing health and safety standards in military contexts.
 
-Given its rarity and specificity, the ANSUR II dataset is an invaluable resource for researchers and policymakers interested in advancing the well-being and effectiveness of female U.S.
+Given its rarity and specificity, the ANSUR II dataset is a vital resource for researchers and policymakers seeking to advance the well-being and effectiveness of female U.S.
 Army personnel.
-By enabling analyses that would otherwise be impossible with civilian datasets, it contributes to a deeper understanding of the unique anthropometric and demographic characteristics of this population, paving the way for evidence-based interventions and policy decisions.
+By enabling analyses that are not possible with civilian datasets, it offers an opportunity to deepen our understanding of the unique anthropometric and demographic characteristics of this population, paving the way for evidence-based interventions and policy decisions.
 
@@
 
-The model's design reflects the characteristics of the dataset to ensure alignment with the nature of the variables and optimize the analysis.
-Anthropometric variables such as height, waist circumference, and thigh circumference were included as continuous predictors to preserve their granularity and maximize sensitivity to subtle variations in body weight.
+The model's design reflects the characteristics of the dataset to ensure alignment with the nature of the variables and improve the analysis.
+Anthropometric variables such as height, waist circumference, and thigh circumference were included as continuous predictors to preserve their granularity and enhance sensitivity to subtle variations in body weight.
 Age was also treated as a continuous variable, rather than being grouped into categories, to avoid arbitrary cutoffs and retain variability, enabling a more precise assessment of its relationship with body weight.
@@
 Additionally, waist and thigh circumferences were rescaled to centimeters for consistency and to reflect standard real-world measurement practices.
-These decisions ensure that the model leverages the dataset's structure effectively while maintaining interpretability and relevance to the research context.
+These decisions ensure that the model effectively utilizes the dataset's structure while maintaining interpretability and relevance to the research context.
 
@@
 
-The Bayesian regression model utilizes default priors provided by the rstanarm package, ensuring robust and reliable inference.
+The Bayesian regression model utilizes default priors provided by the rstanarm package, which facilitate principled and consistent inference.
 These priors are weakly informative, balancing regularization with the flexibility to adapt to the data:
@@
 
-The weakly informative priors are designed to enhance the model's robustness, ensuring credible parameter estimates and reliable uncertainty quantification.
-The use of Bayesian priors provides an added layer of rigor, particularly when estimating complex relationships between predictors and body weight.
-The rstanarm package facilitates the implementation of these priors, making Bayesian inference accessible and effective for this analysis.
+The weakly informative priors are designed to strengthen the model, promoting credible parameter estimates and reliable uncertainty quantification.
+The use of Bayesian priors adds a layer of rigor, particularly when estimating complex relationships between predictors and body weight.
+The rstanarm package supports the implementation of these priors, making Bayesian inference accessible and effective for this analysis.
 
@@
 While this value lacks direct interpretability due to the unrealistic scenario of zero predictors, it provides a conceptual starting point for the model.
-These findings emphasize the importance of anthropometric measurements in predicting body weight while underscoring the need for further exploration of demographic factors to refine the model.
+These results underscore the predictive value of anthropometric measurements in modeling body weight and highlight the necessity of further examining demographic factors to improve the model's explanatory power.
 
@@
 The results emphasize the significant role of anthropometric variables, particularly waist circumference and thigh circumference, as strong predictors of body weight.
-These findings align with previous research, which identify waist circumference as a key indicator of central adiposity and overall body composition [@heymsfield2015], and studies linking thigh circumference to lower body strength and fat distribution [@snijder2005].
-These measurements are critical in the military context, where body composition impacts physical performance and injury risk.
-The observed positive associations reinforce the importance of these variables in health monitoring, fitness interventions, and ergonomic considerations for military equipment design.
+These findings align with previous research identifying waist circumference as a key indicator of central adiposity and overall body composition [@heymsfield2015].
+Central adiposity is known to be associated with higher risks of cardiovascular disease, metabolic disorders, and reduced physical performance, making it an important measurement for monitoring the health of military personnel.
+In physically demanding contexts such as military service, excessive central adiposity can impair mobility, endurance, and the ability to perform tasks under pressure.
+
+Similarly, thigh circumference is a significant indicator of lower body strength and fat distribution, as supported by studies linking larger thigh circumference to greater muscle mass and reduced injury risk [@snijder2005].
+In the military context, strong lower body muscles are essential for activities such as marching, running, lifting heavy equipment, and maintaining stability during combat operations.
+The observed positive associations between thigh circumference and body weight reinforce the importance of maintaining lower body muscle mass to support physical performance and reduce the risk of musculoskeletal injuries.
 
 Although height showed a weaker association with body weight, its inclusion remains biologically plausible.
-Taller individuals typically exhibit larger skeletal structures and greater overall body mass.
-This finding is consistent with literature suggesting that height, while less variable than other anthropometric measures, contributes to baseline estimations of body weight.
+Taller individuals typically exhibit larger skeletal structures, greater lean mass, and increased overall body mass.
+This finding is consistent with literature suggesting that while height is less variable than other anthropometric measures, it contributes to baseline estimations of body weight.
+In practical terms, height serves as an important reference point when assessing body composition, ensuring that weight management programs account for natural variations in skeletal size and proportionality.
+
 These results underscore the nuanced relationships between body composition and demographic factors, offering a foundation for targeted health interventions within military populations.
+For example, female soldiers with higher waist circumference might benefit from interventions focused on core strength and fat reduction, while those with lower thigh circumference might require programs aimed at building lower body muscle mass.
+Such tailored approaches can enhance fitness outcomes and operational readiness, ensuring that all soldiers meet the physical demands of their roles.
 
@@
 
-This research underscores the utility of anthropometric measurements in predicting body weight, providing actionable insights for health monitoring, fitness interventions, and military equipment design.
-For instance, the findings could guide the development of tailored fitness programs to address central adiposity (waist circumference) and muscle mass (thigh circumference), enhancing operational readiness and reducing injury risks.
-These insights align with broader public health objectives, such as the World Health Organization's emphasis on preventing obesity-related conditions through effective weight management strategies.
+This research highlights the utility of anthropometric measurements in predicting body weight, offering practical applications for health monitoring, fitness interventions, and military equipment design.
+For instance, the findings could guide the development of tailored fitness programs to address central adiposity (waist circumference) and muscle mass (thigh circumference), improving operational readiness and reducing injury risks.
+Beyond fitness programs, these findings can inform the design of ergonomic military gear and protective equipment that better accommodates the diverse body shapes and sizes of female soldiers.
+Properly fitted equipment can enhance mobility, comfort, and performance while lowering the risk of injuries caused by ill-fitting gear.
 
-The use of Bayesian regression models in this study further demonstrates the flexibility and interpretability of these methods for investigating complex relationships between biological and demographic factors.
-Bayesian approaches have been increasingly recognized in health research for their ability to incorporate prior knowledge and quantify uncertainty, making them well-suited for studies involving multifactorial predictors.
+These findings align with broader public health objectives, such as the World Health Organization's focus on preventing obesity-related conditions through effective weight management strategies.
+Identifying significant anthropometric predictors of body weight supports initiatives aimed at promoting healthy body composition and reducing the prevalence of chronic diseases.
+For example, routine monitoring of waist and thigh circumference in both military and civilian populations can serve as an early indicator of health risks, prompting timely interventions and lifestyle adjustments.
 
-Looking ahead, integrating more comprehensive datasets and leveraging advanced analytical techniques, such as machine learning or longitudinal modeling, could deepen our understanding of body weight determinants.
-For example, algorithms trained on diverse datasets could identify non-linear patterns and interactions that traditional regression models might overlook.
-Such efforts would not only enhance health outcomes for military personnel but also contribute to broader efforts to improve public health, workplace ergonomics, and fitness standards across diverse populations.
+The use of Bayesian regression models in this study demonstrates the flexibility and interpretability of these methods for analyzing complex relationships between biological and demographic factors.
+Bayesian approaches are particularly beneficial in health research due to their ability to incorporate prior knowledge, quantify uncertainty, and provide probabilistic estimates.
+These features make Bayesian models well-suited for studies involving multifactorial predictors and datasets with inherent variability.
+For instance, Bayesian frameworks can account for uncertainty in measurement data, producing reliable estimates even when sample sizes are limited.
+
+Additionally, Bayesian methods enable the exploration of posterior distributions and credible intervals, offering a deeper understanding of the relationships between predictors and outcomes.
+This level of detail is essential for developing evidence-based policies and interventions that consider variability across different subgroups.
+For example, Bayesian models can identify how the relationship between waist circumference and body weight varies by age group, ethnicity, or military component, enabling more targeted and effective strategies.
 
@@
 
-While this study offers valuable insights, it is subject to certain limitations.
+While this study provides meaningful findings, it is subject to certain limitations.
 First, the dataset focuses exclusively on female U.S.
-Army personnel, limiting the generalizability of findings to male service members or civilian populations.
-Gender differences in body composition and physical fitness have been widely documented, suggesting that extending this analysis to male personnel could uncover additional patterns.
+Army personnel, which limits the applicability of findings to male service members or civilian populations.
+Gender differences in body composition and physical fitness are well-documented, suggesting that extending this analysis to male personnel could reveal additional patterns.
 Future studies should aim to include a more diverse sample, encompassing multiple genders, age groups, and occupational roles.
 
-Second, the dataset does not account for influential lifestyle factors such as physical activity levels, dietary habits, or metabolic rates.
-These variables have been shown to significantly impact body weight and fitness outcomes.
-Including such data could improve the explanatory power and predictive accuracy of future models.
-For example, incorporating wearable fitness trackers or dietary logs might provide richer insights into the interactions between lifestyle behaviors and anthropometric measures.
+Second, the dataset does not include influential lifestyle factors such as physical activity levels, dietary habits, or metabolic rates.
+These variables have been shown to significantly affect body weight and fitness outcomes.
+Including such data could enhance the explanatory power and predictive accuracy of future models.
+For instance, incorporating wearable fitness trackers or dietary logs could provide a deeper understanding of the interactions between lifestyle behaviors and anthropometric measures.
 
-Additionally, while the Bayesian framework offers robust parameter estimates and credible intervals, hierarchical modeling could enhance the analysis by capturing subgroup-specific variations.
-For instance, dependencies within military components or geographic regions could be explored using multilevel Bayesian models, which would allow for greater precision in understanding group-level differences while preserving individual variability.
+Additionally, while the Bayesian framework produces reliable parameter estimates and credible intervals, hierarchical modeling could strengthen the analysis by capturing subgroup-specific variations.
+For example, dependencies within military components or geographic regions could be explored using multilevel Bayesian models, which would allow for greater precision in identifying group-level differences while preserving individual variability.
 
-Expanding the dataset's scope to include longitudinal measurements would also enable researchers to explore dynamic relationships between body composition, fitness, and operational readiness.
-Such studies could inform policies for optimizing physical performance and reducing long-term health risks among service members.
-
+Expanding the dataset's scope to include longitudinal measurements would also enable researchers to study dynamic relationships between body composition, fitness, and operational readiness.
+Such studies could inform policies for improving physical performance and reducing long-term health risks among service members.
 \newpage

### 2024-12-11 paper/paper.qmd
Update paper.qmd
Improve Citation
Update paper.qmd
Check In-text Citations
Polishing Writing in Introduction Section

@@
 [@sec-discussion] discusses the implications, limitations, and future research directions.
-Lastly, [@sec-model-details] offers detailed posterior predictive checks, diagnostic plots, and their interpretations.
+The appendix is divided into three sections: [Appendix -@sec-data-cleaning] discusses the data cleaning process, [Appendix -@sec-model-details] provides additional details of the modeling process, and [Appendix -@sec-ideal-survey] outlines an ideal survey methodology for improved data collection.
 
@@
 
-The ANSUR II dataset provides comprehensive anthropometric and demographic data for 1,986 female U.S [@ANSURII_2012].
+The ANSUR II dataset provides comprehensive anthropometric and demographic data for 1,986 female U.S [@ansurII_2012].
 Army personnel, collected using standardized protocols to ensure accuracy.
@@
 
-# Appendix {.unnumbered}
+# Appendix {-}
 
-# Data Cleaning
+# Data Cleaning {#sec-data-cleaning}
 
@@
 
-# Ideal Survey Methodology
+# Ideal Survey Methodology {#sec-ideal-survey}
 

### 2024-12-11 paper/paper.qmd
Fixing Issues with Cross-Reference, Changing Unnecessary Words

@@
 [@sec-discussion] discusses the implications, limitations, and future research directions.
-The appendix is divided into three sections: [Appendix -@sec-data-cleaning] discusses the data cleaning process, [Appendix -@sec-model-details] provides additional details of the modeling process, and [Appendix -@sec-ideal-survey] outlines an ideal survey methodology for improved data collection.
+Appendix is divided into three sections: [Appendix -@sec-data-cleaning] discusses the data cleaning process, [Appendix -@sec-model-details] provides additional details of the modeling process, and [Appendix -@sec-ideal-survey] outlines an ideal survey methodology for improved data collection.
 
@@
 Height, recorded as heightin in inches, is a key predictor of body weight.
-Taller individuals generally possess larger skeletal structures and greater body mass, making height a crucial variable for understanding variations in weight among the sample population.
+Taller individuals generally possess larger skeletal structures and greater body mass, making height a significant variable for understanding variations in weight among the sample population.
 
@@
 
-Age is a crucial demographic variable in this study, as it encapsulates biological and lifestyle factors that influence body weight.
+Age is an important demographic variable in this study, as it encapsulates biological and lifestyle factors that influence body weight.
 Variations in metabolism, muscle mass, and fat distribution associated with aging play a significant role in shaping body composition.
@@
 
-This comprehensive methodology ensures robust, accurate, and representative data collection while addressing practical, ethical, and logistical considerations.
-By employing stratified random sampling, rigorous data validation, and inclusive recruitment strategies, the study is well-positioned to deliver valuable insights into the determinants of body weight among female U.S.
+This comprehensive methodology facilitates precise, reliable, and representative data collection while addressing practical, ethical, and logistical considerations.
+By employing stratified random sampling, rigorous data validation, and inclusive recruitment strategies, the study is well-positioned to yield meaningful insights into the determinants of body weight among female U.S.
 Army personnel.

### 2024-12-11 other/datasheet/datasheet.qmd
update paper, scripts, references
Specify Clarification on Dataset Usage

--- 2024-11-30 paper/datasheet.qmd
@@
 2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
-    - The dataset was created by the Natick Soldier Research, Development, and Engineering Center (NSRDEC) under the U.S. Army.
+    - The dataset was created by the Natick Soldier Research, Development, and Engineering Center (NSRDEC) on behalf of the U.S. Army as part of the 2012 ANSUR II survey.
 3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
@@
 2. *How many instances are there in total (of each type, if appropriate)?*
-	- The dataset contains 1,986 instances, each representing one soldier.
+	- The dataset contains a total of 1,986 instances, each representing a female U.S. Army personnel. These instances include detailed anthropometric and demographic measurements.
 3.
@@
 5. *Is there a label or target associated with each instance? If so, please provide a description.*
-	- The target variable is body weight (in pounds), which is used to analyze its relationship with the predictors.
+	- Yes, the dataset includes a target variable, weightlbs, which represents the body weight of each individual in pounds.
+This variable serves as the dependent variable in analyses aiming to understand the relationship between body weight and various anthropometric and demographic predictors.
 6.
@@
 8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
-	- No.
+	- Yes, this research uses an 80/20 split, with 80% of the data used as the training set and 20% as the testing set.
+This approach ensures that the model is trained effectively on a majority of the data while retaining a portion for unbiased performance evaluation, as demonstrated by the comparison of RMSE between the full and reduced models.
 9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
-	- The dataset underwent preprocessing to remove noise and redundancies, ensuring high data quality.
+	- Yes, the dataset may have sources of noise such as measurement variability due to inconsistencies in using instruments like calipers and tape measures, as well as missing values that can affect data completeness.
+These issues were addressed by standardizing measurements and removing rows with missing values during preprocessing to ensure accuracy and reliability.
 10.
@@
 Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
-	- The dataset is self-contained and does not rely on external resources.
+	- The dataset is largely self-contained and does not rely on external resources for its core variables, as all data were collected directly through the 2012 ANSUR II Female Dataset.
+While the dataset includes demographic information cross-referenced with administrative records, there are no dependencies on external, dynamically changing resources such as websites or social media.
+The dataset is publicly available and distributed under terms that do not impose restrictions, ensuring accessibility for researchers without licensing fees or additional conditions.
+The archival version of the dataset, as it existed at the time of creation, is well-documented and maintained for consistency.
 11.
@@
 If so, please provide a description.*
-	- No confidential information is included in the dataset.
+	- No, the dataset does not contain data that would typically be considered confidential.
+It includes anthropometric and demographic measurements collected from U.S.
+Army personnel under standardized protocols, but no sensitive personal identifiers or non-public communications are present.
+The data were anonymized to protect individual privacy, ensuring compliance with ethical and legal standards.
 12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
@@
 16. *Any other comments?*
-	- No.
+	- Incorporating additional lifestyle variables such as physical activity levels or dietary habits could enhance its utility and explanatory power in future research.
 
@@
 If not, please describe the timeframe in which the data associated with the instances was created.*
-	- Data was collected between 2010 and 2012, aligning with the time when the measurements were taken.
+	- The data was collected as part of the 2012 ANSUR II survey conducted by the Natick Soldier Research, Development, and Engineering Center.
+The timeframe of data collection aligns with the creation of the dataset, as all measurements and associated demographic information were recorded during the survey period in 2012 using standardized protocols.
+There is no mismatch between the data collection and creation timeframes.
 6.
@@
 If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
-	- Ethical considerations were likely reviewed as part of the U.S. Army's internal processes for human data collection, though explicit documentation is not provided.
+	- The dataset originates from the 2012 ANSUR II survey, conducted by the Natick Soldier Research, Development, and Engineering Center, which followed rigorous ethical standards for data collection.
+Although specific details about an institutional review board (IRB) review are not explicitly mentioned, the data collection adhered to military protocols ensuring participant confidentiality and informed consent.
+These procedures are consistent with ethical guidelines for research involving human subjects in military contexts.
+Supporting documentation, such as the official survey reports, may provide further details and can be accessed through sources like the Natick Soldier Research Center or related publications.
 7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
-	- Website.
+	- The data was obtained by me from the platform Data World, where the 2012 ANSUR II survey dataset is publicly available.
 8.
@@
 1. *Has the dataset been used for any tasks already? If so, please provide a description.*
-	- Cannot find any. 
+	- No, the dataset has not been used for any specific tasks prior to this analysis.
+It was obtained for the purpose of exploring the relationship between body weight and key anthropometric and demographic predictors.
 2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
-	- Cannot find any. 
+	-No, there is no repository that links to papers or systems that use this dataset.
+It was obtained from Data World and does not have an associated archive for tracking its usage in research or systems.
 3. *What (other) tasks could the dataset be used for?*
@@
 If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
-	- Cannot find any.
+	- No, there are no IP-based or other restrictions imposed by third parties on the data associated with the instances.
+The dataset is publicly available on the Data World platform without licensing terms or fees restricting its use.
 6.

### 2024-12-12 paper/paper.qmd
update paper

@@
 
-The ANSUR II dataset provides comprehensive anthropometric and demographic data for 1,986 female U.S [@ansurII_2012].
-Army personnel, collected using standardized protocols to ensure accuracy.
+The ANSUR II dataset provides comprehensive anthropometric and demographic data for 1,986 female U.S.
+Army personnel, collected using standardized protocols to ensure accuracy [@ansurII_2012].
 Unlike civilian datasets, it uniquely addresses the physical demands and characteristics of military personnel, offering valuable information on factors like fitness, injury risk, and gear design [@hotzman2011].
